### 2019-10-30 proposal.Rmd
SUPER ROUGH DRAFT.

---
title: "Seasonal Adaptation Modeling"
author: "Alison Hall, Csenge Petak, & Thomas O'Leary"
date: "10/30/2019"
output: pdf_document
---

## Brief Proposal

Seasonal changes in allele frequency has been observed experimentally in a population of _Drososphila melanagaster_ over the course of three years in an orchard in Pennsylvania (cite). This seasonally fluctuating selection leads to a balanced polymorphism which is one possible mechanism for maintaining genetic diversity over time. It was proposed that the alleles that are under seasonal selection have been maintained for millenia. We thought that modeling these dynamics would be provide insight into the mechanisms involved and the extent to which seasonal selection is capable of maintaining these balanced polymorphisms in the population. Or does the model have to include more complicated features like epistasis and linkage.

We hope to build upon the model developed by (cite). Their model relies upon a mechanishm they call "segregation lift," which necessary "requires seasonal changes in dominance, a phenomenon that may arise naturally in situations with antagonistic pleiotropy and seasonal changes in the relative importance of traits for fitness" (cite). We want to try to fully understand their model and develop something that may incorporate new variables such as linkage.

Perhaps incorporating looking at seasonal adaptation in other model species such as Copepods.

MORE STUFF. BETTER STUFF...

### 2019-10-31 proposal.Rmd
citation added

@@
 output: pdf_document
+bibliography: refs.bib
+biblio-style: science
 ---
@@
 
-Seasonal changes in allele frequency has been observed experimentally in a population of _Drososphila melanagaster_ over the course of three years in an orchard in Pennsylvania (cite).
+Seasonal changes in allele frequency has been observed experimentally in a population of _Drososphila melanagaster_ over the course of three years in an orchard in Pennsylvania [@Bergland2014].
 This seasonally fluctuating selection leads to a balanced polymorphism which is one possible mechanism for maintaining genetic diversity over time.
@@
 
-We hope to build upon the model developed by (cite).
-Their model relies upon a mechanishm they call "segregation lift," which necessary "requires seasonal changes in dominance, a phenomenon that may arise naturally in situations with antagonistic pleiotropy and seasonal changes in the relative importance of traits for fitness" (cite).
+We hope to build upon the model developed by @Bergland2014.
+Their model relies upon a mechanishm they call "segregation lift," which necessary "requires seasonal changes in dominance, a phenomenon that may arise naturally in situations with antagonistic pleiotropy and seasonal changes in the relative importance of traits for fitness" [@Wittmann2017].
 We want to try to fully understand their model and develop something that may incorporate new variables such as linkage.
@@
 
-MORE STUFF. BETTER STUFF...
+--
+
+# References

### 2019-11-03 model_test.R
genome creation, seasonal score & fitness calc

@@ -1,1 +1,74 @@
 # seasonal adaptation modeling -------------------------------------------------
+
+require(tidyverse)
+
+# number of loci in a genome
+L <- 50
+# population size 
+pop_size <- 1
+# dominance
+d <- 0.5
+# exponent of the fitness function? epistasis parameter or something?
+y = 1
+
+
+# initialize diploid chromosomes with a random population with equal allele freq
+genome <- matrix(sample(0:1, 2*L*pop_size, replace = TRUE, prob = c(0.5, 0.5)), 
+                 nrow = pop_size*2, ncol = L)
+
+loci <- paste("locus", str_pad(1:L, 2, "0", side = "left"), sep = "_")
+colnames(genome) <- loci
+
+# name the individuals and their chromosome pairs for dplyr later
+individual <- paste("indiv", 
+                    str_pad(rep(1:pop_size, each = 2), 6, "0", side = "left"), 
+                    sep = "_")
+chr <- paste("chr", rep(1:2, times = pop_size), sep = "_")
+
+# bind the matrix and names together
+genome <- as.tibble(cbind(individual, chr, genome))
+
+# long format for dplyr
+gen_tidy <- genome %>%
+  pivot_longer(cols = contains("locus"), 
+               names_to = "loci", 
+               values_to = "allele")
+
+# sumarize each locus for each inidividual 
+genotype <- gen_tidy %>%
+  group_by(individual, loci) %>%
+  summarize(geno = sum(as.numeric(allele)))
+
+# count of each genotype
+geno_count <- genotype %>%
+  group_by(individual, geno) %>%
+  count()
+
+# seasonal score for each individual
+z_score <- geno_count %>%
+  pivot_wider(names_from = geno, values_from = n) %>%
+  rename("geno_0" = "0", "geno_1" = "1", "geno_2" = "2") %>%
+  mutate(z_winter = geno_0 + geno_1 * d,
+         z_summer = geno_2 + geno_1 * d)
+
+# fitness of each individual
+fitness <- z_score %>%
+  mutate(f_winter = (1 + z_winter) ^ y,
+         f_summer = (1 + z_summer) ^ y)
+
+# selection of the parents 
+# tournament
+# totally random panmictic mating ???
+
+
+
+# crossover 
+cross_prob <- 0.2
+runif(L) < cross_prob
+select(genome, contains("locus"))
+
+
+  
+  
+
+

### 2019-11-04 model_test.R
crossover added

@@ -56,6 +56,7 @@ fitness <- z_score %>%
   mutate(f_winter = (1 + z_winter) ^ y,
          f_summer = (1 + z_summer) ^ y)
 
+
 # selection of the parents 
 # tournament
 # totally random panmictic mating ???
@@ -64,11 +65,13 @@ fitness <- z_score %>%
 
 # crossover 
 cross_prob <- 0.2
-runif(L) < cross_prob
-select(genome, contains("locus"))
+cross <- sample(0:1, pop_size, prob = c(1 - cross_prob, cross_prob))
+cross_loc <- sample(2:L, 1)
+cross_genome <- select(genome, contains("locus"))[1:2, cross_loc:L]
+cross_genome[c(1,2), ] <- cross_genome[c(2,1), ]
+genome[1:2, (length(genome) - length(cross_loc:L) + 1):length(genome)] <- cross_genome
 
 
-  
   
 
 

### 2019-11-04 model_test.R
mutation added -- needs to be cleaned a bit

@@ -62,8 +62,32 @@ fitness <- z_score %>%
 # totally random panmictic mating ???
 
 
+# mutation on the entire population each generation before crossover
+mut_prob <- 0.05 #1*10^(-4)
+
+mut_test_mat <- matrix(runif(L*pop_size*2), 
+                       nrow = pop_size * 2, 
+                       ncol = L)
+mut_pos <- mut_test_mat < mut_prob
+
+mut_vals <- matrix(sample(0:1, 50, replace = TRUE), 
+                   nrow = pop_size * 2, 
+                   ncol = L)
+
+mut_mat <- mut_vals * mut_pos
+
+mat <- matrix(as.numeric(as.matrix(select(genome, contains("locus")))),
+              nrow = pop_size * 2,
+              ncol = L)
+
+par_mat <- mat * !mut_pos
+
+new_mat <- mut_mat + par_mat
+
 
 # crossover 
+# this cross over requires only one parent at a time
+# would it be possible to do all at once, maybe with dplyr real quick??
 cross_prob <- 0.2
 cross <- sample(0:1, pop_size, prob = c(1 - cross_prob, cross_prob))
 cross_loc <- sample(2:L, 1)
@@ -72,6 +96,6 @@ cross_genome[c(1,2), ] <- cross_genome[c(2,1), ]
 genome[1:2, (length(genome) - length(cross_loc:L) + 1):length(genome)] <- cross_genome
 
 
-  
+
 
 

### 2019-11-21 functions.R
chaos user beware

@@ -21,7 +21,6 @@ init_pop <- function(L, pop_size, prob_0 = 0.5, prob_1 = 0.5) {
   return(as_tibble(cbind(individual, chr, genome)))
 }
 
-
 # Funtion to calculate fitness -------------------------------------------------
 fitness_func <- function(genomes, d, y) {
   # creates the diploid genotypes: 0 (homo 00), 1 (het), or 2 (homo 11)
@@ -58,8 +57,7 @@ fitness_func <- function(genomes, d, y) {
 }
 
 # Selecting individuals for the next generation, depends on season -------------
-
-select_inds <- function(genomes,fitness_all, season) {
+select_inds <- function(genomes, fitness_all, season) {
   if (season == "summer") { # select 2 parents at random weighted by fitness
     selected_idx <- sample(seq_len(nrow(fitness_all)), 2, 
                            prob = fitness_all$f_summer, replace = FALSE)
@@ -76,10 +74,10 @@ select_inds <- function(genomes,fitness_all, season) {
 }
 
 # Crossover function that takes a single individual ----------------------------
-cross_over <- function(ind, cross_prob) {
-  # select only the loci or only the indiv and chr identifiers
-  loci <- select(ind, contains("locus"))
-  indiv_chr <- select(ind, -contains("locus"))
+cross_over <- function(parent) {
+  loci <- genomes %>%
+    filter(.$individual == as.character(parent)) %>%
+    select(contains("locus"))
   
   # determine the location(s) for crossover
   cross <- sample(0:1, 
@@ -95,8 +93,40 @@ cross_over <- function(ind, cross_prob) {
     loci[,cross_loc:ncol(loci)] <- cross_genome
   }
   
+  pick_chr <- sample(c(1,2), 1)
+  
   # add back the indiv and chr identifiers
-  return(as_tibble(cbind(indiv_chr, loci)))
+  return(loci[pick_chr, ])
+}
+
+# cross over parents at the same time ------------------------------------------
+cross_over_parents <- function(parent1, parent2) {
+
+  p1_xover <- cross_over(parent1)#, genomes, cross_prob)
+  p2_xover <- cross_over(parent2)#, genomes, cross_prob)
+  
+  new_chr <- rbind(p1_xover, p2_xover)
+  bind_cols("chr" = c("chr_1", "chr_2"), new_chr)
+  
+}
+
+# Parent selection -------------------------------------------------------------
[…]

### 2019-11-21 model_test.R

@@ -1,10 +1,6 @@
 # seasonal adaptation modeling -------------------------------------------------
 
-require(stringr) 
-require(tibble)
-require(tidyr)
-require(dplyr)
-require(ggplot2)
+require(tidyverse)
 
 source("functions.R")
 
@@ -21,13 +17,21 @@ source("functions.R")
 #      (2 = even; < 2 more summer; > 2 more winter)
 
 # Run a simulation -------------------------------------------------------------
+tictoc::tic()
 sim_results <- run_simulation(L = 50, 
                               pop_size = 100,
                               d = 0.5,
                               y = 1, 
                               cross_prob = 0.03,
                               mut_prob = 1*10^(-4),
-                              years = 2,
-                              generations = 5,
+                              years = 1,
+                              generations = 20,
                               seasonal_balance = 2)
+tictoc::toc()
+sim_clean <- sim_results %>%
+  filter(genz %% 10 == 0)
+
+plot_freq(sim_clean, figure_caption = "")
+plot_freq(sim_clean, type = "avg", figure_caption = "")
+
 

### 2019-11-21 model_test.R
test

@@ -31,3 +31,5 @@ sim_results <- run_simulation(L = 50,
                               generations = 5,
                               seasonal_balance = 2)
 
+test
+

### 2019-11-21 model_test.R
for loop for running simulations

@@ -31,3 +31,23 @@ sim_results <- run_simulation(L = 50,
                               generations = 5,
                               seasonal_balance = 2)
 
+
+
+
+numreps <- 1
+d <- c(0.2, 0.5, 0.7)
+sim_results <- sim()
+for (i in 1:numreps){
+  for (k in 1:d){
+run_simulation(L = 5, 
+                                   pop_size = 10,
+                                   d = k,
+                                   y = 1, 
+                                   cross_prob = 0.03,
+                                   mut_prob = 1*10^(-4),
+                                   years = 2,
+                                   generations = 5,
+                                   seasonal_balance = 2)
+  
+  }
+}

### 2019-11-21 functions.R
made results save to a csv

@@ -283,7 +283,7 @@ run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years,
 }
 
 # Simulation -------------------------------------------------------------------
-run_simulation2 <- function(L, pop_size, d, y, cross_prob, mut_prob, years, 
+run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years, 
                            generations, seasonal_balance) {
   # Initialize Population 
   
@@ -348,6 +348,18 @@ run_simulation2 <- function(L, pop_size, d, y, cross_prob, mut_prob, years,
   print(g1)
   g2 <- plot_freq(loci_freq, type = "avg", figure_caption = caption)
   print(g2)
+  
+  file_names <- paste("results",
+                      "G", generations, 
+                      "Ps", pop_size,
+                      "Sb", seasonal_balance,
+                      "L", L,
+                      "d", d,
+                      "y", y,
+                      "c", cross_prob,
+                      sep = "_")
+  
+  write.csv(sim_results,paste0(file_names, ".csv"), row.names = FALSE)
   
   return(loci_freq)
 }

### 2019-11-22 Outline.Rmd
preliminary outline

---
title: "Outline"
author: "Thomas O'Leary, Csenge Petak, Alison Hall"
date: "11/22/2019"
output: pdf_document
---
**Abstract**

The abstract will introduce the paper by Wittman et al. that instigated this 
study. They present a term called "segregation lift" which describes 
instances of seasonal allele-fluctuations which may maintain genetic diversity. 
Wittman et al., build a model that exhibits how allelic dominance changes according to the season in a diploid organism to account for different seasonal life-history strategies. The authors present the parameter d, a dominance metric which enciroporates fitness with the seasonal score to allow the dominance to be tracked as it fluctuates according to season. Wittman et al. conclude that d must be greater than 0.5 allows for a "beneficial reversal of dominance" in which heterozygous intermediates are more fit.

Also present hypothesis here and main results

**Introduction**

- Begin by introducing why we should care about environmental fluctuation and seasonal fitness, how that is projected to grow more and more extreme, and how this study fits into that concept (importance of genetic diversity)
- How this study fits into/differs from research of dominance/heterozygote advantage (clarify this)
- Describe the original concept of seasonal selection in more detail. 
- Present seasonal score  
- Introduce why we changed the parameters that we changed, and how we predicted that segregation lift would be affected. (seasonal score, dominance, generations, population size, y fitness exponent, L loci )

**Methods**

**Results**
Figure 1: Loci specific allele frequencies over time. 
  We have a preliminary version of this graph created and it shows how the frequency of a seasonal allele changes over generations at d=0.5, which suggests that d=0.5 may be sufficient to maintain polymorphism. 
  we plan to run the model over break and change parameters to try to detect how they affect seasonal switches in dominance

Figure 2: A graph encorporating fitness fluctuations?

**Conclusion**

We will interpret the results here!
How does this fit into the broader research

### 2019-11-22 functions.R
added reps to file names

@@ -101,7 +101,7 @@ cross_over <- function(parent) {
 
 # cross over parents at the same time ------------------------------------------
 cross_over_parents <- function(parent1, parent2) {
-
+  
   p1_xover <- cross_over(parent1)#, genomes, cross_prob)
   p2_xover <- cross_over(parent2)#, genomes, cross_prob)
   
@@ -141,19 +141,19 @@ mutate_genome <- function(genomes, mut_prob) {
   
   # determine mutation positions with a random uniform distribution
   mut_pos <- matrix(runif(genome_length * total_chr), 
-                         nrow = total_chr, 
-                         ncol = genome_length) < mut_prob_2
+                    nrow = total_chr, 
+                    ncol = genome_length) < mut_prob_2
   
   # mutation values (with zeros where the original values are located)
   mut_mat <- matrix(sample(0:1, genome_length, replace = TRUE), 
-                     nrow = total_chr, 
-                     ncol = genome_length) * mut_pos
+                    nrow = total_chr, 
+                    ncol = genome_length) * mut_pos
   
   # original values (with zeros where the mutated values are located)
   org_mat <- matrix(as.numeric(as.matrix(select(genomes, contains("locus")))),
-                nrow = total_chr, 
-                ncol = genome_length) * !mut_pos
-
+                    nrow = total_chr, 
+                    ncol = genome_length) * !mut_pos
+  
   # combine matrices by addition
   new_mat <- mut_mat + org_mat
   
@@ -284,7 +284,7 @@ run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years,
 
 # Simulation -------------------------------------------------------------------
 run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years, 
-                           generations, seasonal_balance) {
+                           generations, seasonal_balance, rep) {
   # Initialize Population 
   
   individual <- paste("indiv", 
@@ -309,7 +309,7 @@ run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years,
       fitness_all <- fitness_func(genomes, d, y)
       
       df <- parent_selection(genomes, fitness_all, season)
-
+      
       new_pop <- map2_df(df[[1]], df[[2]], cross_over_parents)
       
       genomes <- cbind(individual, new_pop)
@@ -338,11 +338,11 @@ run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years,
[…]

### 2019-11-22 model_test.R
integrated for loop

@@ -1,6 +1,10 @@
 # seasonal adaptation modeling -------------------------------------------------
 
-require(tidyverse)
+require(stringr) 
+require(tibble)
+require(tidyr)
+require(dplyr)
+require(ggplot2)
 
 source("functions.R")
 
@@ -18,20 +22,22 @@ source("functions.R")
 
 # Run a simulation -------------------------------------------------------------
 tictoc::tic()
-sim_results <- run_simulation(L = 50, 
-                              pop_size = 100,
-                              d = 0.5,
-                              y = 1, 
-                              cross_prob = 0.03,
-                              mut_prob = 1*10^(-4),
-                              years = 1,
-                              generations = 20,
-                              seasonal_balance = 2)
+numreps <- 2
+d <- c(0.2, 0.5, 0.7)
+for (k in d){
+  for (i in 1:numreps){
+    run_simulation(L = 50, 
+                   pop_size = 100,
+                   d = k,
+                   y = 1, 
+                   cross_prob = 0.03,
+                   mut_prob = 1*10^(-4),
+                   years = 1,
+                   generations = 20,
+                   seasonal_balance = 2,
+                   rep = i)
+    
+  }
+}
 tictoc::toc()
-sim_clean <- sim_results %>%
-  filter(genz %% 10 == 0)
-
-plot_freq(sim_clean, figure_caption = "")
-plot_freq(sim_clean, type = "avg", figure_caption = "")
-
 

### 2019-11-22 functions.R
cleaning up

@@ -56,23 +56,6 @@ fitness_func <- function(genomes, d, y) {
   return(fitness)
 }
 
-# Selecting individuals for the next generation, depends on season -------------
-select_inds <- function(genomes, fitness_all, season) {
-  if (season == "summer") { # select 2 parents at random weighted by fitness
-    selected_idx <- sample(seq_len(nrow(fitness_all)), 2, 
-                           prob = fitness_all$f_summer, replace = FALSE)
-  } else {
-    selected_idx <- sample(seq_len(nrow(fitness_all)), 2, 
-                           prob = fitness_all$f_winter, replace = FALSE)
-  }
-  temp1 <- selected_idx*2-1
-  temp2 <-selected_idx*2
-  ind1 <- genomes[temp1[1]:temp2[1],] #because we want both chrs
-  ind2 <- genomes[temp1[2]:temp2[2],]
-  selected_individuals <- list(ind1,ind2)
-  return(selected_individuals)
-}
-
 # Crossover function that takes a single individual ----------------------------
 cross_over <- function(parent) {
   loci <- genomes %>%
@@ -210,80 +193,6 @@ plot_freq <- function(loci_freq, type = "loci", figure_caption) {
 
 # Simulation -------------------------------------------------------------------
 run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years, 
-                           generations, seasonal_balance) {
-  # Initialize Population 
-  
-  genomes <- init_pop(L, pop_size) 
-  freq_df <- get_freqs(genomes, pop_size)
-  
-  G <- 1
-  for (year in 1:years){
-    for (generation in 1:generations){
-      if (generation < generations / seasonal_balance){
-        season <- "summer"
-      } else {
-        season <- "winter"
-      }
-      # create an empty population data frame with all zeros
-      new_pop <- init_pop(L, pop_size, prob_0 = 1, prob_1 = 0)
-      fitness_all <- fitness_func(genomes, d, y)
-      for (i in 1:pop_size){
-        # select parents based on fitness
-        selected_for_mating <- select_inds(genomes, fitness_all, season)
-        # cross chromosomes of parents
-        crossed1 <- cross_over(selected_for_mating[[1]], cross_prob)
-        new_ind_chr1 <- crossed1[sample(seq_len(nrow(crossed1)), 1),]
-        crossed2 <- cross_over(selected_for_mating[[2]], cross_prob)
[…]

### 2019-11-23 model_test.R
added parameter values to test

@@ -23,7 +23,13 @@ source("functions.R")
 # Run a simulation -------------------------------------------------------------
 tictoc::tic()
 numreps <- 2
-d <- c(0.2, 0.5, 0.7)
+d <- c(0.2, 0.5, 0.8)
+num_generations <- c(10,20,50)
+cross_over_nums <- c(0.01, 0.05, 0.1)
+pops <- c(100,1000,10000)
+y <- c(0.5,1.0,2.0)
+sesss <- c(1.25,1.5,2.0)
+
 for (k in d){
   for (i in 1:numreps){
     run_simulation(L = 50, 
@@ -40,24 +46,4 @@ for (k in d){
   }
 }
 tictoc::toc()
-
-
-
-numreps <- 1
-d <- c(0.2, 0.5, 0.7)
-sim_results <- sim()
-for (i in 1:numreps){
-  for (k in 1:d){
-run_simulation(L = 5, 
-                                   pop_size = 10,
-                                   d = k,
-                                   y = 1, 
-                                   cross_prob = 0.03,
-                                   mut_prob = 1*10^(-4),
-                                   years = 2,
-                                   generations = 5,
-                                   seasonal_balance = 2)
-  
-  }
-}
 

### 2019-11-23 model_test.R
set default parameters

@@ -23,23 +23,23 @@ source("functions.R")
 
 # Run a simulation -------------------------------------------------------------
 tictoc::tic()
-numreps <- 2
-d <- c(0.2, 0.5, 0.8)
-num_generations <- c(10,20,50)
-cross_over_nums <- c(0.01, 0.05, 0.1)
-pops <- c(100,1000,10000)
-y <- c(0.5,1.0,2.0)
-sesss <- c(1.25,1.5,2.0)
+numreps <- 20
+d <- c(0.2, 0.5, 0.8) #Tom
+num_generations <- c(10,20,50) #Tom
+cross_over_nums <- c(0.01, 0.05, 0.1, 0.5) #Csenge
+pops <- c(100,1000,10000) #Alison
+y <- c(0.5,1.0,2.0) #Alison
+seas_bal <- c(1.25,1.5,2.0) #Csenge
 
 for (k in d){
   for (i in 1:numreps){
-    run_simulation(L = 50, 
-                   pop_size = 100,
-                   d = k,
+    run_simulation(L = 250, 
+                   pop_size = 1000,
+                   d = 0.5,
                    y = 1, 
-                   cross_prob = 0.03,
+                   cross_prob = 0.05,
                    mut_prob = 1*10^(-4),
-                   years = 1,
+                   years = 300,
                    generations = 20,
                    seasonal_balance = 2,
                    rep = i)
@@ -47,4 +47,17 @@ for (k in d){
   }
 }
 tictoc::toc()
+
+#default parameters
+# 
+# (L = 250, 
+#   pop_size = 1000,
+#   d = 0.5,
+#   y = 1, 
+#   cross_prob = 0.05,
+#   mut_prob = 1*10^(-4),
+#   years = 300,
+#   generations = 20,
+#   seasonal_balance = 2,
+#   rep = i)
 

### 2019-11-23 Alison_job.R
set up individual jobs

@@ -1,0 +1,74 @@
+# seasonal adaptation modeling -------------------------------------------------
+
+require(stringr) 
+require(tibble)
+require(tidyr)
+require(dplyr)
+require(ggplot2)
+require(purrr)
+
+source("functions.R")
+
+# Parameter definitions --------------------------------------------------------
+# L is the number of loci in a genome
+# pop_size is the population size 
+# d is the dominance parameter of the heterozygote
+# y is the exponent of the fitness function
+# cross_prob is the recombination rate
+# mut_prob is the mutation rate
+# years is the duration of experiment in years
+# generations is the number of generations in a season
+# seasonal_balance is the balance between seasons
+#      (2 = even; < 2 more summer; > 2 more winter)
+
+# Run a simulation -------------------------------------------------------------
+
+numreps <- 20
+pops <- c(100,1000,10000) #Alison
+y <- c(0.5,1.0,2.0) #Alison
+
+for (k in pops){
+  for (i in 1:numreps){
+    run_simulation(L = 250, 
+                   pop_size = k,
+                   d = 0.5,
+                   y = 1, 
+                   cross_prob = 0.05,
+                   mut_prob = 1*10^(-4),
+                   years = 300,
+                   generations = 20,
+                   seasonal_balance = 2,
+                   rep = i)
+    
+  }
+}
+for (k in y){
+  for (i in 1:numreps){
+    run_simulation(L = 250, 
+                   pop_size = 1000,
+                   d = 0.5,
+                   y = k, 
+                   cross_prob = 0.05,
+                   mut_prob = 1*10^(-4),
+                   years = 300,
+                   generations = 20,
+                   seasonal_balance = 2,
+                   rep = i)
+    
+  }
+}
+
+
+#default parameters
+# 
+# (L = 250, 
+#   pop_size = 1000,
+#   d = 0.5,
+#   y = 1, 
+#   cross_prob = 0.05,
+#   mut_prob = 1*10^(-4),
+#   years = 300,
+#   generations = 20,
+#   seasonal_balance = 2,
+#   rep = i)
+

### 2019-11-23 Csenge_job.R

@@ -1,0 +1,75 @@
+# seasonal adaptation modeling -------------------------------------------------
+
+require(stringr) 
+require(tibble)
+require(tidyr)
+require(dplyr)
+require(ggplot2)
+require(purrr)
+
+source("functions.R")
+
+# Parameter definitions --------------------------------------------------------
+# L is the number of loci in a genome
+# pop_size is the population size 
+# d is the dominance parameter of the heterozygote
+# y is the exponent of the fitness function
+# cross_prob is the recombination rate
+# mut_prob is the mutation rate
+# years is the duration of experiment in years
+# generations is the number of generations in a season
+# seasonal_balance is the balance between seasons
+#      (2 = even; < 2 more summer; > 2 more winter)
+
+# Run a simulation -------------------------------------------------------------
+
+numreps <- 20
+cross_over_nums <- c(0.01, 0.05, 0.1, 0.5) #Csenge
+seas_bal <- c(1.25,1.5,2.0) #Csenge
+
+for (k in cross_over_nums){
+  for (i in 1:numreps){
+    run_simulation(L = 250, 
+                   pop_size = 1000,
+                   d = 0.5,
+                   y = 1, 
+                   cross_prob = k,
+                   mut_prob = 1*10^(-4),
+                   years = 300,
+                   generations = 20,
+                   seasonal_balance = 2,
+                   rep = i)
+    
+  }
+}
+
+for (k in seas_bal){
+  for (i in 1:numreps){
+    run_simulation(L = 250, 
+                   pop_size = 1000,
+                   d = 0.5,
+                   y = 1, 
+                   cross_prob = 0.05,
+                   mut_prob = 1*10^(-4),
+                   years = 300,
+                   generations = 20,
+                   seasonal_balance = k,
+                   rep = i)
+    
+  }
+}
+
+
+#default parameters
+# 
+# (L = 250, 
+#   pop_size = 1000,
+#   d = 0.5,
+#   y = 1, 
+#   cross_prob = 0.05,
+#   mut_prob = 1*10^(-4),
+#   years = 300,
+#   generations = 20,
+#   seasonal_balance = 2,
+#   rep = i)
+

### 2019-11-23 Tom_job.R

@@ -1,0 +1,73 @@
+# seasonal adaptation modeling -------------------------------------------------
+
+require(stringr) 
+require(tibble)
+require(tidyr)
+require(dplyr)
+require(ggplot2)
+require(purrr)
+
+source("functions.R")
+
+# Parameter definitions --------------------------------------------------------
+# L is the number of loci in a genome
+# pop_size is the population size 
+# d is the dominance parameter of the heterozygote
+# y is the exponent of the fitness function
+# cross_prob is the recombination rate
+# mut_prob is the mutation rate
+# years is the duration of experiment in years
+# generations is the number of generations in a season
+# seasonal_balance is the balance between seasons
+#      (2 = even; < 2 more summer; > 2 more winter)
+
+# Run a simulation -------------------------------------------------------------
+
+numreps <- 20
+d <- c(0.2, 0.5, 0.8) #Tom
+num_generations <- c(10,20,50) #Tom
+
+for (k in d){
+  for (i in 1:numreps){
+    run_simulation(L = 250, 
+                   pop_size = 1000,
+                   d = k,
+                   y = 1, 
+                   cross_prob = 0.05,
+                   mut_prob = 1*10^(-4),
+                   years = 300,
+                   generations = 20,
+                   seasonal_balance = 2,
+                   rep = i)
+    
+  }
+}
+for (k in num_generations){
+  for (i in 1:numreps){
+    run_simulation(L = 250, 
+                   pop_size = 1000,
+                   d = 0.5,
+                   y = 1, 
+                   cross_prob = 0.05,
+                   mut_prob = 1*10^(-4),
+                   years = 300,
+                   generations = k,
+                   seasonal_balance = 2,
+                   rep = i)
+    
+  }
+}
+
+#default parameters
+# 
+# (L = 250, 
+#   pop_size = 1000,
+#   d = 0.5,
+#   y = 1, 
+#   cross_prob = 0.05,
+#   mut_prob = 1*10^(-4),
+#   years = 300,
+#   generations = 20,
+#   seasonal_balance = 2,
+#   rep = i)
+

### 2019-11-23 Csenge_job.R
changed variables to make it faster

@@ -23,19 +23,19 @@ source("functions.R")
 
 # Run a simulation -------------------------------------------------------------
 
-numreps <- 20
+numreps <- 2
 cross_over_nums <- c(0.01, 0.05, 0.1, 0.5) #Csenge
 seas_bal <- c(1.25,1.5,2.0) #Csenge
 
 for (k in cross_over_nums){
   for (i in 1:numreps){
-    run_simulation(L = 250, 
-                   pop_size = 1000,
+    run_simulation(L = 100, 
+                   pop_size = 500,
                    d = 0.5,
                    y = 1, 
                    cross_prob = k,
                    mut_prob = 1*10^(-4),
-                   years = 300,
+                   years = 100,
                    generations = 20,
                    seasonal_balance = 2,
                    rep = i)
@@ -45,13 +45,13 @@ for (k in cross_over_nums){
 
 for (k in seas_bal){
   for (i in 1:numreps){
-    run_simulation(L = 250, 
-                   pop_size = 1000,
+    run_simulation(L = 100, 
+                   pop_size = 500,
                    d = 0.5,
                    y = 1, 
                    cross_prob = 0.05,
                    mut_prob = 1*10^(-4),
-                   years = 300,
+                   years = 100,
                    generations = 20,
                    seasonal_balance = k,
                    rep = i)
@@ -60,16 +60,4 @@ for (k in seas_bal){
 }
 
 
-#default parameters
-# 
-# (L = 250, 
-#   pop_size = 1000,
-#   d = 0.5,
-#   y = 1, 
-#   cross_prob = 0.05,
-#   mut_prob = 1*10^(-4),
-#   years = 300,
-#   generations = 20,
-#   seasonal_balance = 2,
-#   rep = i)
 

### 2019-11-23 Outline.Rmd

@@
 - Begin by introducing why we should care about environmental fluctuation and seasonal fitness, how that is projected to grow more and more extreme, and how this study fits into that concept (importance of genetic diversity)
+  -seasonal fluctuation has been shown to maintain polymorphisms, but hoe often is this really able to occur. 
+  -"marginal overdominance occurs when when the heterozygote has the highest geometric mean fitness, though in one particular generation the homozygote may be most fit" (witt), and seasonal fluctuations are capable of maintaining these advantages (novak)This novak paper found that linkage disequilibrium was required to maintain genetic polymorphims though
 - How this study fits into/differs from research of dominance/heterozygote advantage (clarify this)

### 2019-11-23 writing/manuscript.Rmd
create folders

---
title: "Seasonal Adaptation"
author: \emph{Thomas O'Leary, Csenge Petak, Alison Hall}
date: "11/23/2019"
output: pdf_document
bibliography: refs.bib
---

# Abstract

# Introduction
Something about an orchard in Pennsylvania [@Bergland2014]. As an example of how to cite.

# Methods

# Results

# Discussion

# References

### 2019-11-23 scripts/Tom_job.R

@@ -23,7 +23,7 @@ source("functions.R")
 
 # Run a simulation -------------------------------------------------------------
 
-numreps <- 2
+numreps <- 5
 d <- c(0.2, 0.5, 0.8) #Tom
 num_generations <- c(10,20,50) #Tom
 
@@ -42,20 +42,20 @@ for (k in d){
     
   }
 }
-for (k in num_generations){
-  for (i in 1:numreps){
-    run_simulation(L = 100, 
-                   pop_size = 500,
-                   d = 0.5,
-                   y = 1, 
-                   cross_prob = 0.05,
-                   mut_prob = 1*10^(-4),
-                   years = 100,
-                   generations = k,
-                   seasonal_balance = 2,
-                   rep = i)
-    
-  }
-}
+# for (k in num_generations){
+#   for (i in 1:numreps){
+#     run_simulation(L = 100, 
+#                    pop_size = 500,
+#                    d = 0.5,
+#                    y = 1, 
+#                    cross_prob = 0.05,
+#                    mut_prob = 1*10^(-4),
+#                    years = 100,
+#                    generations = k,
+#                    seasonal_balance = 2,
+#                    rep = i)
+#     
+#   }
+# }
 
 

### 2019-11-23 writing/manuscript.Rmd
table options

@@
 bibliography: refs.bib
+header-includes:
+   - \usepackage{graphicx}
 ---
@@
 
+\begin{table}[t]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{|l|l|}
+\hline
+Parameters                       &      \\ \hline
+Crossover probability            & 0.05 \\ \hline
+Mutation probability             & 10   \\ \hline
+Population size                  & 500  \\ \hline
+Number of loci                   & 100  \\ \hline
+Exponent of the fitness function & 1    \\ \hline
+Dominance                        & 0.5  \\ \hline
+Years                            & 100  \\ \hline
+Generations per year             & 20   \\ \hline
+Seasonal balance                 & 2    \\ \hline
+\end{tabular}%
+}
+\caption{The default parameters that were used for each simulation.}
+\label{tab:my-table}
+\end{table}
+
+| Parameters                       |      |
+|----------------------------------|------|
+| Crossover probability            | 0.05 |
+| Mutation probability             | 10   |
+| Population size                  | 500  |
+| Number of loci                   | 100  |
+| Exponent of the fitness function | 1    |
+| Dominance                        | 0.5  |
+| Years                            | 100  |
+| Generations per year             | 20   |
+| Seasonal balance                 | 2    |
+
 # Results

### 2019-11-23 writing/manuscript.Rmd
parameter table added

--- 2019-11-23 writing/manuscript.Rmd
@@
 
+| Default Parameters               |      |
+|----------------------------------|------|
+| Crossover probability            | 0.05 |
+| Mutation probability             | 10   |
+| Population size                  | 500  |
+| Number of loci                   | 100  |
+| Exponent of the fitness function | 1    |
+| Dominance                        | 0.5  |
+| Years                            | 100  |
+| Generations per year             | 20   |
+| Seasonal balance                 | 2    |
+
 # Results

### 2019-11-25 writing/manuscript.Rmd
some rough methods added

@@
 
+### Basic Model
+
+The method for calculating fitness is based on the work of @Wittmann2017 who originally proposed “segregation lift” as a general mechanism which may maintain balanced polymorphisms in a population under certain conditions.
+
+The model first determines an individual's seasonal score ($z$) according to the equation: write equations later :)
+
+where $n_{homo}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci.
+A dominance parameter of greater than one ($d > 1$) would correspond to a traditional heterozygote advantage, and therefore is not of interest in this model.
+
+The model we propose differs from the _segregation lift model_ in a few important ways.
+For one, the loci in our model are located on diploid linked chromosomes, so the homologous pairs can recombine during a simulated meiosis before mating.
+Expand on why this may be interesting or important… Linked genes not require a $d > 0.5$.
+Some genes that may be important for seasonal traits (_i.e._ heat shock proteins) are located close to each other on chromosomes and have a high amount of linkage disequilibrium…
+
+Our model also does not allow for “selfing” where an individual can asexually reproduce with itself to create an offspring… Other stufff maybe too
+
 | Default Parameters               |      |
@@
 
+### Simulated seasonal selection
+
+The general outline for the seasonal selection simulation:
+
+1. A population of $N$ individuals is created with a single diploid chromosome containing $L$ loci, all of which contribute to the individual’s seasonal fitness. 
+2. Seasonal score is calculated according to Eqn 1 and the fitness is determined
+Pairs of parents – of size $N$ – are sampled stochasticly with a probability proportional to their seasonal fitness. 
+3. Each parent in the pair undergoes recombination with a per locus recombination rate of $P_c$ 
+4. A chromosome from each parent is selected at random to create the diploid offsprings 
+5. The new generation replaces the old generation in the population.
+6. The new individuals undergo mutation with a per locus mutation probability $P_m$ which was fixed at the relatively high rate of 1x10^-14 [@Haag-Liautard2007]. 
+7. A new generation begins and the current season is determined by the current generation and seasonal balance parameter $S_b$. 
+8. A new generation of parents is selected according to their seasonal fitness and the process continues to cycle for a number of years.
+9. Loci specific allele frequencies are tracked throughout the simulated evolutionary run.
+
 # Results

### 2019-11-26 functions.R
uniform crossover functions added

@@ -93,6 +93,41 @@ cross_over_parents <- function(parent1, parent2) {
   
 }
 
+
+# uniform crossover function ---------------------------------------------------
+cross_over_uniform <- function(parent) {
+  loci <- genomes %>%
+    filter(.$individual == as.character(parent)) %>%
+    select(contains("locus"))
+  
+  # determine the location(s) for crossover
+  cross <- sample(1:2, 
+                  ncol(loci), 
+                  prob = c(0.5, 0.5), 
+                  replace = TRUE)
+  
+  new_chr <- vector(mode = "double", length = ncol(loci))
+  for (i in 1:length(cross)){
+    new_chr[i] <- as.numeric(loci[cross[i], i])
+  }
+  
+  names(new_chr) <- names(loci)
+  
+  return(new_chr)
+}
+
+# cross over parents at the same time ------------------------------------------
+cross_over_parents_uniform <- function(parent1, parent2) {
+  
+  p1_xover <- cross_over_uniform(parent1)
+  p2_xover <- cross_over_uniform(parent2)
+  
+  new_chr <- as_tibble(rbind(p1_xover, p2_xover))
+  bind_cols("chr" = c("chr_1", "chr_2"), new_chr)
+  
+}
+
+
 # Parent selection -------------------------------------------------------------
 parent_selection <- function(genomes, fitness_all, season){
   if (season == "summer"){
@@ -275,3 +310,86 @@ run_simulation <- function(L, pop_size, d, y, cross_prob, mut_prob, years,
 }
 
 
+
+# simulation with uniform crossover --------------------------------------------
+run_simulation_uniform <- function(L, pop_size, d, y, cross_prob, mut_prob, 
+                                   years, generations, seasonal_balance, rep) {
+  # Initialize Population 
+  
+  individual <- paste("indiv", 
+                      str_pad(rep(1:pop_size, each = 2), 
+                              6, "0", side = "left"), 
+                      sep = "_")
+  
+  cross_prob <<- cross_prob
+  genomes <<- init_pop(L, pop_size) 
+  freq_df <- get_freqs(genomes, pop_size)
+  
+  G <- 1
+  for (year in 1:years){
+    for (generation in 1:generations){
+      if (generation < generations / seasonal_balance){
+        season <- "summer"
+      } else {
+        season <- "winter"
+      }
+      # create an empty population data frame with all zeros
+      new_pop <- init_pop(L, pop_size, prob_0 = 1, prob_1 = 0)
[…]

### 2019-11-26 functions.R
plot_freq title argument added

@@ -196,7 +196,8 @@ get_freqs <- function(genomes, pop_size){
 }
 
 # Plotting allele frequencies overtime -----------------------------------------
-plot_freq <- function(loci_freq, type = "loci", figure_caption) {
+plot_freq <- function(loci_freq, type = "loci", figure_caption,
+                      fig_title = "Loci specific allele frequencies over time"){
   if (type == "avg"){
     avg_freq <- loci_freq %>%
       group_by(genz) %>%
@@ -204,7 +205,7 @@ plot_freq <- function(loci_freq, type = "loci", figure_caption) {
     
     g <- ggplot(avg_freq, mapping = aes(x = genz, y = freqs)) + 
       geom_line() +
-      labs(title = "Total summer allele frequency over time",
+      labs(title = fig_title,
            caption = figure_caption) +
       xlab("Generations") +
       ylab("Freq of Summer Allele") + 
@@ -215,7 +216,7 @@ plot_freq <- function(loci_freq, type = "loci", figure_caption) {
     plot_df <- loci_freq
     g <- ggplot(plot_df, mapping = aes(x = genz, y = freqs, color = loci)) + 
       geom_line() +
-      labs(title = "Loci specific allele frequencies over time",
+      labs(title = fig_title,
            caption = figure_caption)+
       xlab("Generations") +
       ylab("Freq of Summer Allele") + 

### 2019-11-26 scripts/analysis.R
script for plotting and analysis

@@ -1,0 +1,49 @@
+# results analysis -------------------------------------------------------------
+
+require(tidyverse)
+
+source(here::here("functions.R"))
+
+# set working directory to the results folder of interest
+setwd(here::here("results/dominance"))
+
+# get a list of the files that match the variable value of interest
+value <- "d_0.2"
+
+# which rep do you want to look at? 
+rep <- 1
+
+# find files that match and create figure captions with parameter details
+files <- list.files()[grep(value, list.files())]
+names <- str_remove(files, ".csv")
+param <- str_split(names, "_", simplify = TRUE)[,c(3,5,7,9,11,13,15,18)]
+caption <- paste(paste("Generations per year", param[rep, 1]),
+                paste("Pop size", param[rep, 2]),
+                paste("Seasonal Balance", param[rep, 3]),
+                paste("Number of Loci", paste0(param[rep, 4], "\n")),
+                paste("Dominance", param[rep, 5]),
+                paste("Epistasis", param[rep, 6]),
+                paste("Crossover probability", param[rep, 7]),
+                paste("Replicate number", param[rep, 8]), sep = "; ")
+
+
+# read in file and plot results
+sim_results <- read.csv(files[rep])
+
+# plot results less than generation 2000
+sim_results %>%
+  filter(genz < 2000) %>%
+  plot_freq(figure_caption = caption, fig_title = value)
+
+# plot results between genz 5000 and 6000
+sim_results %>%
+  filter(genz > 5000 & genz < 6000) %>%
+  plot_freq(figure_caption = caption, fig_title = value)
+
+
+
+
+
+
+
+

### 2019-11-26 scripts/analysis.R
proportion of loci at fixation plot added

@@ -20,8 +20,8 @@ param <- str_split(names, "_", simplify = TRUE)[,c(3,5,7,9,11,13,15,18)]
 caption <- paste(paste("Generations per year", param[rep, 1]),
                 paste("Pop size", param[rep, 2]),
                 paste("Seasonal Balance", param[rep, 3]),
-                paste("Number of Loci", paste0(param[rep, 4], "\n")),
-                paste("Dominance", param[rep, 5]),
+                paste("Number of Loci", param[rep, 4]),
+                paste("\nDominance", param[rep, 5]),
                 paste("Epistasis", param[rep, 6]),
                 paste("Crossover probability", param[rep, 7]),
                 paste("Replicate number", param[rep, 8]), sep = "; ")
@@ -35,10 +35,30 @@ sim_results %>%
   filter(genz < 2000) %>%
   plot_freq(figure_caption = caption, fig_title = value)
 
-# plot results between genz 5000 and 6000
+# plot results less than generation 2000 and divisible by 10 to get only the 
+# freq at the seasonal turns for gen/year = 20
 sim_results %>%
-  filter(genz > 5000 & genz < 6000) %>%
+  filter(genz < 2000 & genz %% 10 == 0) %>%
   plot_freq(figure_caption = caption, fig_title = value)
+
+# plot results between genz 500 and 600
+sim_results %>%
+  filter(genz > 500 & genz < 600) %>%
+  plot_freq(figure_caption = caption, fig_title = value)
+
+
+# plot the proportion of loci at fixation
+sim_results %>%
+  filter(genz < 6000) %>%
+  group_by(genz) %>%
+  filter(freqs == 0 | freqs == 1) %>%
+  count() %>%
+  mutate(freqs = n / as.numeric(param[rep, 4])) %>%
+  ggplot(mapping = aes(x = genz, y = freqs)) +
+  geom_line() + 
+  ylim(0, 1) +
+  ylab("Propotion of fixed loci") +
+  xlab("Generations")
 
 
 

### 2019-11-27 scripts/analysis.R
created a function that takes your parameters and gives you boxplots and ANOVA results

@@ -1,17 +1,18 @@
 # results analysis -------------------------------------------------------------
 
 require(tidyverse)
+require(rlist)
 
 source(here::here("functions.R"))
 
 # set working directory to the results folder of interest
-setwd(here::here("results/dominance"))
+setwd(here::here("results/generations"))
 
 # get a list of the files that match the variable value of interest
-value <- "d_0.2"
+value <- "G_20"
 
 # which rep do you want to look at? 
-rep <- 1
+rep <- 3
 
 # find files that match and create figure captions with parameter details
 files <- list.files()[grep(value, list.files())]
@@ -43,7 +44,7 @@ sim_results %>%
 
 # plot results between genz 500 and 600
 sim_results %>%
-  filter(genz > 500 & genz < 600) %>%
+  filter(genz > 900 & genz < 1000) %>%
   plot_freq(figure_caption = caption, fig_title = value)
 
 
@@ -60,10 +61,102 @@ sim_results %>%
   ylab("Propotion of fixed loci") +
   xlab("Generations")
 
+# histogram at generation 6000 (if possible)
+sim_results <- sim_results[sim_results$genz == max(sim_results$genz),]
+hist(sim_results$freqs)
+mean(sim_results$freqs)
+sd(sim_results$freqs)
 
+# COMPARE different parameters ----------------------------------------------------------------
 
+setwd(here::here("results/generations"))
+values = c("G_10","G_20","G_50") #this needs to be of length 3 and of increasing order
+do_analysis(values) #first boxplot = means, second boxplot = standard deviation, categories appear
+                    #in the order you put it in the values variable above
+                    #also gives you 3 ANOVA: first means, second standard deviation, third ratio of fixed loci
 
-
-
-
-
+#first run function below, then call it
+do_analysis <- function(values){
+  
+  files = c()
+  for (value in values){
+    file <- list.files()[grep(value, list.files())]
+    files <- list.append(files, file) #contains all the files regarding your parameter in the correct order
+  }
+  
+  sim_results <- vector(mode = "list", length = 15)
+  i = 1
+  for (f in files){
+    sim_result <- read.csv(f)
[…]

### 2019-11-29 scripts/analysis.R
added extra way of visualisation (during Skype meeting)

@@ -6,10 +6,10 @@ require(rlist)
 source(here::here("functions.R"))
 
 # set working directory to the results folder of interest
-setwd(here::here("results/generations"))
+setwd(here::here("results/generation"))
 
 # get a list of the files that match the variable value of interest
-value <- "G_20"
+value <- "G_50"
 
 # which rep do you want to look at? 
 rep <- 3
@@ -42,9 +42,14 @@ sim_results %>%
   filter(genz < 2000 & genz %% 10 == 0) %>%
   plot_freq(figure_caption = caption, fig_title = value)
 
+sim_results %>%
+  filter(loci %in% as.character(sample(unique(sim_results$loci), 10, replace = FALSE))) %>%
+  filter(genz > 2000 & genz < 2100 & genz %% 10 == 0) %>%
+  plot_freq(figure_caption = caption, fig_title = value)
+
 # plot results between genz 500 and 600
 sim_results %>%
-  filter(genz > 900 & genz < 1000) %>%
+  filter(genz > 2800 & genz < 3000) %>%
   plot_freq(figure_caption = caption, fig_title = value)
 
 
@@ -69,8 +74,8 @@ sd(sim_results$freqs)
 
 # COMPARE different parameters ----------------------------------------------------------------
 
-setwd(here::here("results/generations"))
-values = c("G_10","G_20","G_50") #this needs to be of length 3 and of increasing order
+setwd(here::here("results/cross_over"))
+values = c("c_0_","c_0.1","c_0.5") #this needs to be of length 3 and of increasing order
 do_analysis(values) #first boxplot = means, second boxplot = standard deviation, categories appear
                     #in the order you put it in the values variable above
                     #also gives you 3 ANOVA: first means, second standard deviation, third ratio of fixed loci

### 2019-11-30 functions.R
moved do analysis function

@@ -394,3 +394,96 @@ run_simulation_uniform <- function(L, pop_size, d, y, cross_prob, mut_prob,
   
   #return(loci_freq)
 }
+
+# analysis & ANOVA plotting function -------------------------------------------
+do_analysis <- function(values){
+  
+  files = c()
+  for (value in values){
+    file <- list.files()[grep(value, list.files())]
+    files <- list.append(files, file) #contains all the files regarding your parameter in the correct order
+  }
+  
+  sim_results <- vector(mode = "list", length = 15)
+  i = 1
+  for (f in files){
+    sim_result <- read.csv(f)
+    sim_results[i] <- list(sim_result) #contains all dataframes of your parameter (length = 15)
+    i <- i+1
+  }
+  
+  maximums <- c()
+  for (rep in sim_results){
+    maximums <- list.append(maximums, max(rep$genz)) #this ensures that the minimum of all the maximum generations is used for analysis
+  }
+  
+  means <- c()
+  standard_devs <- c()
+  for (rep in sim_results){
+    temp <- rep[rep$genz == min(maximums),] #check that all have same max generation!
+    means <- list.append(means, mean(temp$freqs))
+    standard_devs <- list.append(standard_devs, sd(temp$freqs))
+  }
+  
+  means1 <- means[1:5] #means of loci frequency when parameter = first input value
+  means2 <- means[6:10] #means of loci frequency when parameter = second input value
+  means3 <- means[11:15] #means of loci frequency when parameter = third input value
+  
+  x <- data.frame("Categories" = c("Means1","Means1","Means1","Means1","Means1",
+                                   "Means2","Means2","Means2","Means2","Means2",
+                                   "Means3","Means3","Means3","Means3","Means3"),
+                  "Means" = c(means1,means2,means3))
+  
+  ANOVAofmeans <- aov(x$Means ~ x$Categories)
+  print(summary(ANOVAofmeans))
+  
+  boxplot(x$Means ~ x$Categories,
+          ylab="Mean loci frequency",
+          xlab= "Dominance values", #REPLACE THIS
+          names=c("d = 0.2","d = 0.5","d = 0.8"), #REPLACE THIS
+          col= c("gray", "blue", "green")
[…]

### 2019-11-30 scripts/analysis.R
do_analysis moved. and density plots created. messy!

@@ -6,7 +6,7 @@ require(rlist)
 source(here::here("functions.R"))
 
 # set working directory to the results folder of interest
-setwd(here::here("results/generation"))
+setwd(here::here("results/generations"))
 
 # get a list of the files that match the variable value of interest
 value <- "G_50"
@@ -80,88 +80,57 @@ do_analysis(values) #first boxplot = means, second boxplot = standard deviation,
                     #in the order you put it in the values variable above
                     #also gives you 3 ANOVA: first means, second standard deviation, third ratio of fixed loci
 
-#first run function below, then call it
-do_analysis <- function(values){
-  
-  files = c()
-  for (value in values){
-    file <- list.files()[grep(value, list.files())]
-    files <- list.append(files, file) #contains all the files regarding your parameter in the correct order
-  }
-  
-  sim_results <- vector(mode = "list", length = 15)
-  i = 1
-  for (f in files){
-    sim_result <- read.csv(f)
-    sim_results[i] <- list(sim_result) #contains all dataframes of your parameter (length = 15)
-    i <- i+1
-  }
-  
-  maximums <- c()
-  for (rep in sim_results){
-    maximums <- list.append(maximums, max(rep$genz)) #this ensures that the minimum of all the maximum generations is used for analysis
-  }
-    
-  means <- c()
-  standard_devs <- c()
-  for (rep in sim_results){
-    temp <- rep[rep$genz == min(maximums),] #check that all have same max generation!
-    means <- list.append(means, mean(temp$freqs))
-    standard_devs <- list.append(standard_devs, sd(temp$freqs))
-  }
-  
-  means1 <- means[1:5] #means of loci frequency when parameter = first input value
-  means2 <- means[6:10] #means of loci frequency when parameter = second input value
-  means3 <- means[11:15] #means of loci frequency when parameter = third input value
-  
-  x <- data.frame("Categories" = c("Means1","Means1","Means1","Means1","Means1","Means2","Means2","Means2","Means2","Means2","Means3","Means3","Means3","Means3","Means3"), "Means" = c(means1,means2,means3))
-  
[…]

### 2019-11-30 functions.R
read_plus func

@@ -487,3 +487,9 @@ do_analysis <- function(values){
   ) 
 }
 
+# read csv and save file name for tbl in map_df --------------------------------
+read_plus <- function(flnm) {
+  read_csv(flnm) %>% 
+    mutate(filename = flnm)
+}
+

### 2019-11-30 scripts/analysis.R
cleaned up the density plotting

@@ -88,49 +88,21 @@ do_analysis(values) #first boxplot = means, second boxplot = standard deviation,
 # set working directory to the results folder of interest
 setwd(here::here("results/dominance"))
 
-# filter only the final generation
-
-tbl <- list.files(pattern = value) %>% 
-  map_df(~read_plus(.))
-
-
-
+# load all files and filter only the final generation
 all_tbl <- list.files() %>% 
-  map_df(~read_plus(.))
-
-read_plus <- function(flnm) {
-  read_csv(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-p <- all_tbl %>%
+  map_df(~read_plus(.)) %>%
   filter(genz == max(genz)) 
-
-y <- all_tbl %>% 
-  pivot_wider(
-    names_from = filename,
-    values_from = freqs) %>%
-  select(contains("d_0.8"))
-
-colors <- c(rep("#e25dbb", 5), 
-            rep("#6cdf4c", 5),
-            rep("#258bd2", 5))
-
 
 # plot the density distribution
 ggplot(p, aes(x = freqs, fill = filename)) +
   geom_density(alpha = 0.2) + 
-  scale_fill_manual(values = colors,
+  scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                               rep("#6cdf4c", 5),
+                               rep("#258bd2", 5)),
                     breaks = unique(all_tbl$filename)[c(1,6,11)],
                     name = "Dominance",
                     labels = c("0.2", "0.5", "0.8")) +
   ylab("Density") + 
   xlab("Allele Frequency") +
   theme_classic()
-  
 
-x <- shapiro.test(p$freqs)
-
-x$p.value
-
-# so load all five reps, label them with another column and then group them and stack on top of eachother

### 2019-11-30 scripts/analysis.R
epistasis. But for variables like gens/year needs to be more flexible for other max gen values maybe split() or $ would work with that

@@ -86,7 +86,7 @@ do_analysis(values) #first boxplot = means, second boxplot = standard deviation,
 # histogram and density plots --------------------------------------------------
 
 # set working directory to the results folder of interest
-setwd(here::here("results/dominance"))
+setwd(here::here("results/generations"))
 
 # load all files and filter only the final generation
 all_tbl <- list.files() %>% 
@@ -94,13 +94,15 @@ all_tbl <- list.files() %>%
   filter(genz == max(genz)) 
 
 # plot the density distribution
-ggplot(p, aes(x = freqs, fill = filename)) +
+ggplot(all_tbl, aes(x = freqs, fill = filename)) +
   geom_density(alpha = 0.2) + 
   scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                rep("#6cdf4c", 5),
                                rep("#258bd2", 5)),
                     breaks = unique(all_tbl$filename)[c(1,6,11)],
+                    # legend name
                     name = "Dominance",
+                    # values tested
                     labels = c("0.2", "0.5", "0.8")) +
   ylab("Density") + 
   xlab("Allele Frequency") +

### 2019-11-30 scripts/analysis.R
dynamic way to get the last generations

@@ -90,8 +90,11 @@ setwd(here::here("results/generations"))
 
 # load all files and filter only the final generation
 all_tbl <- list.files() %>% 
-  map_df(~read_plus(.)) %>%
-  filter(genz == max(genz)) 
+  map_df(~read_plus(.)) 
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))})
 
 # plot the density distribution
 ggplot(all_tbl, aes(x = freqs, fill = filename)) +
@@ -101,9 +104,9 @@ ggplot(all_tbl, aes(x = freqs, fill = filename)) +
                                rep("#258bd2", 5)),
                     breaks = unique(all_tbl$filename)[c(1,6,11)],
                     # legend name
-                    name = "Dominance",
+                    name = "Epistasis",
                     # values tested
-                    labels = c("0.2", "0.5", "0.8")) +
+                    labels = c("0.5", "1", "2")) +
   ylab("Density") + 
   xlab("Allele Frequency") +
   theme_classic()

### 2019-11-30 scripts/analysis.R
cool dynamic way to filter the data

@@ -94,19 +94,20 @@ all_tbl <- list.files() %>%
 
 tbl_max_gen <- all_tbl %>%
   split(.$filename) %>%
-  map(function(.data){filter(.data, genz == max(genz))})
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
 
 # plot the density distribution
-ggplot(all_tbl, aes(x = freqs, fill = filename)) +
+ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
   geom_density(alpha = 0.2) + 
   scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                rep("#6cdf4c", 5),
                                rep("#258bd2", 5)),
                     breaks = unique(all_tbl$filename)[c(1,6,11)],
                     # legend name
-                    name = "Epistasis",
+                    name = "Generations\nper year",
                     # values tested
-                    labels = c("0.5", "1", "2")) +
+                    labels = c("10", "20", "50")) +
   ylab("Density") + 
   xlab("Allele Frequency") +
   theme_classic()

### 2019-11-30 writing/manuscript.Rmd

@@
 ---
-title: "Seasonal Adaptation"
+title: "The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation"
 author: \emph{Thomas O'Leary, Csenge Petak, Alison Hall}
-date: "11/23/2019"
-output: pdf_document
+output: 
+  pdf_document:
+    number_sections: true
 bibliography: refs.bib
@@
    - \usepackage{graphicx}
+   - \usepackage{float}
 ---
+
+```{r global_options, include=FALSE}
+knitr::opts_chunk$set(fig.pos = 'H',
+                      fig.height = 3,
+                      fig.width = 5)
+
+require(tidyverse)
+source(here::here("functions.R"))
+```
 
@@
 
-### Basic Model
+## Basic Model
 
-The method for calculating fitness is based on the work of @Wittmann2017 who originally proposed “segregation lift” as a general mechanism which may maintain balanced polymorphisms in a population under certain conditions.
+The method for calculating fitness is based on the work of @Wittmann2017 who originally proposed _segregation lift_ as a general mechanism which may maintain balanced polymorphisms in a population under certain conditions.
 
-The model first determines an individual's seasonal score ($z$) according to the equation: write equations later :)
+The model first determines an individual's seasonal score ($z$) according to the equation:
 
+$$
+z = n_{homo} + d * n_{het}
+$$
 where $n_{homo}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci.
@@
 
-The model we propose differs from the _segregation lift model_ in a few important ways.
+The model we propose differs from the _segregation lift_ model in a few important ways.
 For one, the loci in our model are located on diploid linked chromosomes, so the homologous pairs can recombine during a simulated meiosis before mating.
@@
 | Default Parameters               |           |
-|----------------------------------|------|
+|----------------------------------|-----------|
 | Crossover probability            | 0.05      |
-| Mutation probability             | 10   |
+| Mutation probability             | $10^{-4}$ |
 | Population size                  | 500       |
@@
 
-### Simulated seasonal selection
+## Simulated seasonal selection
 
@@
 
+## Crossover rate
+
+## Epistasis
+
+This is how you reference Figure \ref{epi_density} in the text.
+
+```{r, fig.cap = 'Generations \\label{epi_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/epistasis"))
+
+# load all files and filter only the final generation
+all_tbl <- list.files() %>% 
+  map_df(~read_plus(.))
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
+
+# plot the density distribution
+ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+  geom_density(alpha = 0.2) + 
+  scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                               rep("#6cdf4c", 5),
+                               rep("#258bd2", 5)),
+                    breaks = unique(all_tbl$filename)[c(1,6,11)],
+                    # legend name
+                    name = "Epistasis",
+                    # values tested
+                    labels = c("0.5", "1", "2")) +
+  ylab("Density") + 
+  xlab("Allele Frequency") +
+  theme_classic()
+
+```
+
+## Dominance
+
+## Generations per season
+
+This is how you reference Figure \ref{gen_density} in the text.
+
+```{r, fig.cap = 'Generations \\label{gen_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/generations"))
+
+# load all files and filter only the final generation
+all_tbl <- list.files() %>% 
+  map_df(~read_plus(.))
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
+
+# plot the density distribution
+ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+  geom_density(alpha = 0.2) + 
+  scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                               rep("#6cdf4c", 5),
+                               rep("#258bd2", 5)),
+                    breaks = unique(all_tbl$filename)[c(1,6,11)],
+                    # legend name
+                    name = "Generations\nper year",
+                    # values tested
+                    labels = c("10", "20", "50")) +
+  ylab("Density") + 
+  xlab("Allele Frequency") +
+  theme_classic()
+
+```
+
+## Seasonal balance
+
+## Population size
+
 # Discussion

### 2019-11-30 writing/manuscript.Rmd
figures

@@
                       fig.height = 3,
-                      fig.width = 5)
+                      fig.width = 6.5)
 
 require(tidyverse)
+require(cowplot)
 source(here::here("functions.R"))
@@
 # plot the density distribution
-ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+p1 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
         geom_density(alpha = 0.2) + 
@@
 # plot the density distribution
-ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+p2 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
         geom_density(alpha = 0.2) + 
@@
 
+```{r, fig.cap = 'Generations \\label{density_combined}', message = FALSE, echo = FALSE}
+plot_grid(p1, p2, labels = "AUTO")
+```
+
 ## Seasonal balance

### 2019-12-01 functions.R
made the do_analysis function take any number of variables and automatically do the labelling for the graphs

@@ -396,7 +396,7 @@ run_simulation_uniform <- function(L, pop_size, d, y, cross_prob, mut_prob,
 }
 
 # analysis & ANOVA plotting function -------------------------------------------
-do_analysis <- function(values){
+do_analysis <- function(values, test_name){
   
   files = c()
   for (value in values){
@@ -404,11 +404,11 @@ do_analysis <- function(values){
     files <- list.append(files, file) #contains all the files regarding your parameter in the correct order
   }
   
-  sim_results <- vector(mode = "list", length = 15)
+  sim_results <- vector(mode = "list", length = length(values))
   i = 1
   for (f in files){
     sim_result <- read.csv(f)
-    sim_results[i] <- list(sim_result) #contains all dataframes of your parameter (length = 15)
+    sim_results[i] <- list(sim_result) #contains all dataframes of your parameter
     i <- i+1
   }
   
@@ -416,6 +416,8 @@ do_analysis <- function(values){
   for (rep in sim_results){
     maximums <- list.append(maximums, max(rep$genz)) #this ensures that the minimum of all the maximum generations is used for analysis
   }
+  
+#------------------------------------------------------------------------------------------------------
   
   means <- c()
   standard_devs <- c()
@@ -425,40 +427,49 @@ do_analysis <- function(values){
     standard_devs <- list.append(standard_devs, sd(temp$freqs))
   }
   
-  means1 <- means[1:5] #means of loci frequency when parameter = first input value
-  means2 <- means[6:10] #means of loci frequency when parameter = second input value
-  means3 <- means[11:15] #means of loci frequency when parameter = third input value
+  lm <- length(means)/5 #number of parameters to compare
+  t <- list(1:lm)
   
-  x <- data.frame("Categories" = c("Means1","Means1","Means1","Means1","Means1",
-                                   "Means2","Means2","Means2","Means2","Means2",
-                                   "Means3","Means3","Means3","Means3","Means3"),
-                  "Means" = c(means1,means2,means3))
+#Calculating means--------------------------------------------------------------------------------------
+  
[…]

### 2019-12-01 scripts/analysis.R
now do_analysis can be used more freely

@@ -75,8 +75,8 @@ sd(sim_results$freqs)
 # COMPARE different parameters ----------------------------------------------------------------
 
 setwd(here::here("results/cross_over"))
-values = c("c_0_","c_0.1","c_0.5") #this needs to be of length 3 and of increasing order
-do_analysis(values) #first boxplot = means, second boxplot = standard deviation, categories appear
+values = c("c_0_", "c_0.001_", "c_0.01","c_0.05", "c_0.1","d_0.5_y_1_c_0.5_") #this needs to be of length 3 and of increasing order
+do_analysis(values, "cross_over") #first boxplot = means, second boxplot = standard deviation, categories appear
                     #in the order you put it in the values variable above
                     #also gives you 3 ANOVA: first means, second standard deviation, third ratio of fixed loci
 

### 2019-12-01 scripts/analysis.R
commented

@@ -74,11 +74,9 @@ sd(sim_results$freqs)
 
 # COMPARE different parameters ----------------------------------------------------------------
 
-setwd(here::here("results/cross_over"))
-values = c("c_0_", "c_0.001_", "c_0.01","c_0.05", "c_0.1","d_0.5_y_1_c_0.5_") #this needs to be of length 3 and of increasing order
-do_analysis(values, "cross_over") #first boxplot = means, second boxplot = standard deviation, categories appear
-                    #in the order you put it in the values variable above
-                    #also gives you 3 ANOVA: first means, second standard deviation, third ratio of fixed loci
+setwd(here::here("results/dominance"))
+values = c("d_0.2", "d_0.5", "d_0.8")
+do_analysis(values, "Dominance") # Dominance is going to be the x axis label
 
 
 

### 2019-12-01 writing/manuscript.Rmd

@@
 ```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H',
-                      fig.height = 3,
-                      fig.width = 6.5)
+knitr::opts_chunk$set(fig.pos = 'H')
 
@@
 
-```{r, fig.cap = 'Generations \\label{epi_density}', message = FALSE, echo = FALSE}
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter.
+\\label{epi_density}', message = FALSE, echo = FALSE}
 setwd(here::here("results/epistasis"))
@@
 # load all files and filter only the final generation
-all_tbl <- list.files() %>% 
+all_tbl <- list.files(pattern = "c_0.05") %>% 
   map_df(~read_plus(.))
@@
 
+print(p1)
+
 ```
@@
 
-## Generations per season
+This is how you reference Figure \ref{dom_density} in the text.
 
-This is how you reference Figure \ref{gen_density} in the text.
-
-```{r, fig.cap = 'Generations \\label{gen_density}', message = FALSE, echo = FALSE}
-setwd(here::here("results/generations"))
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of dominance.
+\\label{dom_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/dominance"))
 
@@
                           # legend name
+                          name = "Dominance",
+                          # values tested
+                          labels = c("0.2", "0.5", "0.8")) +
+        ylab("Density") + 
+        xlab("Allele Frequency") +
+        theme_classic()
+
+print(p2)
+
+```
+
+## Generations per season
+
+This is how you reference Figure \ref{gen_density} in the text.
+
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year.
+\\label{gen_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/generations"))
+
+# load all files and filter only the final generation
+all_tbl <- list.files() %>% 
+  map_df(~read_plus(.))
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
+
+# plot the density distribution
+p3 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+        geom_density(alpha = 0.2) + 
+        scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                                     rep("#6cdf4c", 5),
+                                     rep("#258bd2", 5)),
+                          breaks = unique(all_tbl$filename)[c(1,6,11)],
+                          # legend name
                           name = "Generations\nper year",
@@
 
+print(p3)
 ```
 
-```{r, fig.cap = 'Generations \\label{density_combined}', message = FALSE, echo = FALSE}
+```{r, fig.height = 3, fig.width = 8 , fig.cap = 'A density plot of the allele frequencies at the final generation \\label{density_combined}', message = FALSE, echo = FALSE}
+
+# this is how you could potentially mash a few figures together in the same plot
 plot_grid(p1, p2, labels = "AUTO")

### 2019-12-01 functions.R
modified do_analysis so that a specific boxplot can be returned

@@ -396,7 +396,7 @@ run_simulation_uniform <- function(L, pop_size, d, y, cross_prob, mut_prob,
 }
 
 # analysis & ANOVA plotting function -------------------------------------------
-do_analysis <- function(values, test_name){
+do_analysis <- function(values, test_name, boxplot_n){
   
   files = c()
   for (value in values){
@@ -448,12 +448,17 @@ do_analysis <- function(values, test_name){
     c <- c + 1
   }
   
+  #b1 <- ggplot(x, aes(x=test_name, y="Mean loci frequency")) + 
+    geom_boxplot()
+  
   boxplot(x$Means ~ x$Categories,
           ylab="Mean loci frequency",
           xlab= test_name,
           names= v_names,
           col= v_colors
   )
+  b1 <- recordPlot()
+  
   
 #Calculating standard deviation-------------------------------------------------------------------------
   
@@ -468,6 +473,7 @@ do_analysis <- function(values, test_name){
           names= v_names,
           col= v_colors
   )
+  b2 <- recordPlot()
   
 #Calculating fixed proportions---------------------------------------------------------------------------
   
@@ -489,7 +495,17 @@ do_analysis <- function(values, test_name){
           names= v_names,
           col= v_colors
   )
+  b3 <- recordPlot()
   
+  if (boxplot_n == "b1"){
+    return(b1)
+  }
+  else if (boxplot_n == "b2"){
+    return(b2)
+  }
+  else {
+    return(b3)
+  }
 }
 
 # read csv and save file name for tbl in map_df --------------------------------

### 2019-12-01 scripts/analysis.R
corrected useage of do_analysis

@@ -6,10 +6,10 @@ require(rlist)
 source(here::here("functions.R"))
 
 # set working directory to the results folder of interest
-setwd(here::here("results/generations"))
+setwd(here::here("results/cross_over"))
 
 # get a list of the files that match the variable value of interest
-value <- "G_50"
+value <- "d_0.8_y_1_c_0.5"
 
 # which rep do you want to look at? 
 rep <- 3
@@ -40,7 +40,7 @@ sim_results %>%
 # freq at the seasonal turns for gen/year = 20
 sim_results %>%
   filter(genz < 2000 & genz %% 10 == 0) %>%
-  plot_freq(figure_caption = caption, fig_title = value)
+  plot_freq(figure_caption = caption, fig_title = "Dominance = 0.8, no linkage" )
 
 sim_results %>%
   filter(loci %in% as.character(sample(unique(sim_results$loci), 10, replace = FALSE))) %>%
@@ -74,10 +74,10 @@ sd(sim_results$freqs)
 
 # COMPARE different parameters ----------------------------------------------------------------
 
-setwd(here::here("results/dominance"))
-values = c("d_0.2", "d_0.5", "d_0.8")
-do_analysis(values, "Dominance") # Dominance is going to be the x axis label
-
+setwd(here::here("results/cross_over"))
+values = c("d_0.5_y_1_c_0.5", "d_0.8_y_1_c_0.5")
+b <- do_analysis(values, "Dominance", "b2") # Dominance is going to be the x axis label, if boxplot number = b3 the third boxplot will be returned
+b
 
 
 

### 2019-12-01 writing/manuscript.Rmd
started writing up results section

@@
 require(cowplot)
+require(rlist)
+require(png) 
+require(knitr)
 source(here::here("functions.R"))
@@
 # Results
+
+We first tested whether we were succsessful in reimplementing the model made by @Wittmann2017.
+We too found that with no linkage (i.e.
+cross-over happens at every loci) the both proportion of fixed loci (p = 2.52e-07) and standard deviation of loci frequencies (p = 4.63e-07) are lower when dominance is 0.8 compared to when dominance is 0.5.
+
+```{r, message = FALSE, include=FALSE}
+setwd(here::here("results/cross_over"))
+values = c("d_0.5_y_1_c_0.5", "d_0.8_y_1_c_0.5")
+b <- do_analysis(values, "Dominance", "b2") # Dominance is going to be the x axis label, if boxplot number = b3 the third boxplot will be returned
+```
+```{r, echo = FALSE}
+b
+```
+
+```{r, fig.width = 2}
+# Small fig.width
+knitr::include_graphics("D05C05.png")
+knitr::include_graphics("D08C05.png")
+```
 

### 2019-12-01 writing/Outline.Rmd

--- 2019-11-23 Outline.Rmd
@@
 **Introduction**
+
+Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity (cooper).
+Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions (Gulisija).
+Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally (novak, bergland).
+Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions (fournier-level).
+  There has been some debate regarding whether balancing selection is capable of maintaining genetic polymorphisms in highly variable environments, and it is often thought that  (Asthana, Hedrick).
+However a study by Bergland et al (2014) observing Drosophila melanogaster in a temperate Pennsyvanian orchard revealed that strong seasonal selection can drive balancing selection favoring different life history traits over a short time span.
+These results suggest that seasonal variation contributes to the maintenance of two alleles to be present at the same loci long-term.
+  Wittmann et al, (2017) created a model building from Bergland et al to clarify the role of seasonal selection plays in maintaining multilocus polymorphisms.
+This model introduces the term “segregation lift” which considers the importance of dominance in maintaining polymorphism across many loci in the genome.
 

### 2019-12-02 writing/manuscript.Rmd
added intro

--- 2019-12-01 writing/manuscript.Rmd
@@
 # Introduction
-Something about an orchard in Pennsylvania [@Bergland2014]. As an example of how to cite.
+
+Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2014].
+Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016].
+Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].
+Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].
+
+There has been some debate regarding whether balancing selection is capable of maintaining genetic polymorphisms in highly variable environments, and it is often thought that  this mechanism alone is not enough to maintain balanced polymorphism.
+(@Asthana2005, @Hedrick).
+However a study by @Bergland2014 observing Drosophila melanogaster in a temperate Pennsyvanian orchard revealed that strong seasonal selection can drive balancing selection favoring different life history traits over a short time span.
+These results suggest that seasonal variation contributes to the maintenance of two alleles to be present at the same loci long-term.
+If there is no fitness cost associated with polymorphic variation and there is a benefit gained through heterozygosity, then it is suggested that that balancing selection could preserve genetic variation [@Asthana2005, @Wittman2017].
+
+@Wittman2017 created a model simulating the seasonal selection observed by @Bergland2014 to clarify the role this allelic fluctuation plays in maintaining multilocus polymorphisms.
+This model introduces the term “segregation lift” which considers the importance of dominance in maintaining polymorphism across many loci in the genome and proposes that segregation lift plays an important role in preserving genetic variation.
+
+Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
+We study how rate of crossover, epistasis, allelic dominance, and seasonal balance contributes to segregation lift.
 

### 2019-12-02 functions.R
fixed labeling of boxplots

@@ -396,7 +396,7 @@ run_simulation_uniform <- function(L, pop_size, d, y, cross_prob, mut_prob,
 }
 
 # analysis & ANOVA plotting function -------------------------------------------
-do_analysis <- function(values, test_name, boxplot_n){
+do_analysis <- function(values, test_name, vtest, boxplot_n){
   
   files = c()
   for (value in values){
@@ -404,6 +404,31 @@ do_analysis <- function(values, test_name, boxplot_n){
     files <- list.append(files, file) #contains all the files regarding your parameter in the correct order
   }
   
+  print(files)
+  
+  if (vtest == "c_"){
+    strip_values <- sub(".*c_", "", values)
+    strip_values <- sub("_", "", strip_values)
+  } else if (vtest == "d_"){
+    strip_values <- sub(".*d_", "", values)
+    strip_values <- sub("_", "", strip_values)
+  } else if (vtest == "G_"){
+    strip_values <- sub(".*G_", "", values)
+    strip_values <- sub("_", "", strip_values)
+  } else if (vtest == "Ps_"){
+    strip_values <- sub(".*Ps_", "", values)
+    strip_values <- sub("_", "", strip_values)
+  } else if (vtest == "Sb_"){
+    strip_values <- sub(".*Sb_", "", values)
+    strip_values <- sub("_", "", strip_values)
+  } else if (vtest == "y"){
+    strip_values <- sub(".*y_", "", values)
+    strip_values <- sub("_", "", strip_values)
+  } else {
+    strip_values <- values
+  }
+  
+
   sim_results <- vector(mode = "list", length = length(values))
   i = 1
   for (f in files){
@@ -427,6 +452,8 @@ do_analysis <- function(values, test_name, boxplot_n){
     standard_devs <- list.append(standard_devs, sd(temp$freqs))
   }
   
+  print(means)
+  
   lm <- length(means)/5 #number of parameters to compare
   t <- list(1:lm)
   
@@ -442,14 +469,13 @@ do_analysis <- function(values, test_name, boxplot_n){
   p_colors = c("gray", "blue", "green", "yellow", "red", "orange", "purple", "white", "black", "pink")
   v_colors = c()
   c <- 1
-  for (v in values){
+  for (v in strip_values){
     v_names <- list.append(v_names, v)
     v_colors <- list.append(v_colors, p_colors[c])
     c <- c + 1
   }
   
[…]

### 2019-12-02 writing/manuscript.Rmd
Continnued with results sections

--- 2019-12-01 writing/manuscript.Rmd
@@
 
+We first tested whether we were succsessful in reimplementing the model made by @Wittmann2017.
+We too found that with no linkage (i.e.
+cross-over happens at every loci) both the proportion of fixed loci (p = 2.52e-07) and standard deviation of loci frequencies (p = 4.63e-07) are lower when dominance is 0.8 compared to when dominance is 0.5.
+
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter.
+\\label{epi_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/cross_over"))
+
+# load all files and filter only the final generation
+all_tbl <- list.files(pattern = "c_0.5") %>% 
+  map_df(~read_plus(.))
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
+
+# plot the density distribution
+p1 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+        geom_density(alpha = 0.2) + 
+        scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                                     rep("#6cdf4c", 5)),
+                          breaks = unique(all_tbl$filename)[c(1,6)],
+                          # legend name
+                          name = "Dominance",
+                          # values tested
+                          labels = c("0.5", "0.8")) +
+        ylab("Density") + 
+        xlab("Allele Frequency") +
+        theme_classic()
+
+print(p1)
+
+```
+
+```{r, fig.width = 10}
+# Small fig.width
+knitr::include_graphics("D05C05.png")
+knitr::include_graphics("D08C05.png")
+```
+
+Then, we started playing with different parameters.
 ## Crossover rate
 
+Crossover rate didn't seem to have an effect at all in terms of standard deviation (p = 0.123) and proportion of fixed loci (p = 0.462).
+Our hypothesis is that crossover didn't have an effect because two opposing forces created by it canceled out.
+First of all, higher crossover rates creates more genetic variation in the population "helping" selection but on the other hand it also creates stochasticity since a selected high fitness individual can pass on an unfit chromosome after crossover by chance.
+
+When there was no crossover and so linkage was maximized there was a much bigger variation in the proportion of fixed loci in the last generation.
+This could be because since in this case the only way for an individual to change was through mutations, which is pretty infrequent, if the starting population contained a lot of individuals with more of one allele than the other many loci went to fixation while in a starting population with individuals whose genomes contained 50%-50% of the two alleles balancing polymorphism could be maintained more successfully.
+
+```{r, message = FALSE, include=FALSE}
+setwd(here::here("results/cross_over"))
+values = c("c_0_", "c_0.001", "c_0.01_", "c_0.05","c_0.1", "d_0.5_y_1_c_0.5_")
+b <- do_analysis(values, "Dominance", "c_", "b3")
+```
+```{r, echo = FALSE}
+b
+```
+
+## Dominance
+
+Since the crossover rate didn't have an effect on whether or not balanced polymorphism is achieved, our tests with different dominance values resulted in the same dynamics as when we tested with crossover rate 0.5.
+
+This is how you reference Figure \ref{dom_density} in the text.
+
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of dominance.
+\\label{dom_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/dominance"))
+
+# load all files and filter only the final generation
+all_tbl <- list.files() %>% 
+  map_df(~read_plus(.))
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
+
+# plot the density distribution
+p2 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+        geom_density(alpha = 0.2) + 
+        scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                                     rep("#6cdf4c", 5),
+                                     rep("#258bd2", 5)),
+                          breaks = unique(all_tbl$filename)[c(1,6,11)],
+                          # legend name
+                          name = "Dominance",
+                          # values tested
+                          labels = c("0.2", "0.5", "0.8")) +
+        ylab("Density") + 
+        xlab("Allele Frequency") +
+        theme_classic()
+
+print(p2)
+
+```
+
 ## Epistasis
+
+Under default crossover rate (0.05) epistasis didn't have an effect (standard deviation p = 0.986, proportion of fixed alleles p = 0.613).
 
@@
 
-## Dominance
+## Generations per season
 
-This is how you reference Figure \ref{dom_density} in the text.
-
-```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of dominance.
-\\label{dom_density}', message = FALSE, echo = FALSE}
-setwd(here::here("results/dominance"))
-
-# load all files and filter only the final generation
-all_tbl <- list.files() %>% 
-  map_df(~read_plus(.))
-
-tbl_max_gen <- all_tbl %>%
-  split(.$filename) %>%
-  map(function(.data){filter(.data, genz == max(genz))}) %>%
-  do.call("rbind", .)
-
-# plot the density distribution
-p2 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
-        geom_density(alpha = 0.2) + 
-        scale_fill_manual(values = c(rep("#e25dbb", 5), 
-                                     rep("#6cdf4c", 5),
-                                     rep("#258bd2", 5)),
-                          breaks = unique(all_tbl$filename)[c(1,6,11)],
-                          # legend name
-                          name = "Dominance",
-                          # values tested
-                          labels = c("0.2", "0.5", "0.8")) +
-        ylab("Density") + 
-        xlab("Allele Frequency") +
-        theme_classic()
-
-print(p2)
-
-```
-
-## Generations per season
+When the generations per season was 10, the standard deviation was significantly lower than for longer generation times per season (p = 0.00161).
+We hypothise that with more generations per season loci were under selection for a longer period of time and thus were more likely to go to fixation at one point.
 
@@
 
+```{r, fig.width = 10}
+# Small fig.width
+knitr::include_graphics("G10.png")
+knitr::include_graphics("G50.png")
+```
+
+## Population size
+
+Population size had the biggest effect by far (standard deviation p = 1.51e-10, proportion of fixed loci p = 1.63e-10).
+Purely by changing population size from 100 to 1000 average proportion of fixed loci decreased from 0.9 to 0.3.
+This is probably due to the effect of random genetic drift; when the population is small alleles go to fixation due to the large effect of drift.
+
+```{r}
+setwd(here::here("results/pop_size"))
+values = c("Ps_100_", "Ps_500", "Ps_1000")
+b <- do_analysis(values, "Generations per semester", "Ps_", "b3")
+```
+```{r, echo = FALSE}
+b
+```
+
+## Seasonal balance
+
+Interestingly, having a season that has more generations than in the other didn't result in a higher proportion of fixed alleles as one whould have expected (p = 0.289).
+Rather, while alleles fixed by reaching frequencies of 0 or 1 in the case where both seasons had equal number of generations (seasonal balance = 2) when there were more generations in one more alleles had frequencies of 1 than 0 but the overall proportion stayed the same.
+
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year.
+\\label{gen_density}', message = FALSE, echo = FALSE}
+setwd(here::here("results/seasonal_balance"))
+
+# load all files and filter only the final generation
+all_tbl <- list.files() %>% 
+  map_df(~read_plus(.))
+
+tbl_max_gen <- all_tbl %>%
+  split(.$filename) %>%
+  map(function(.data){filter(.data, genz == max(genz))}) %>%
+  do.call("rbind", .)
+
+# plot the density distribution
+p3 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
+        geom_density(alpha = 0.2) + 
+        scale_fill_manual(values = c(rep("#e25dbb", 5), 
+                                     rep("#6cdf4c", 5),
+                                     rep("#258bd2", 5)),
+                          breaks = unique(all_tbl$filename)[c(1,6,11)],
+                          # legend name
+                          name = "Generations\nper year",
+                          # values tested
+                          labels = c("1.25", "1.5", "2")) +
+        ylab("Density") + 
+        xlab("Allele Frequency") +
+        theme_classic()
+
+print(p3)
+
+```
+
+## Mutational interaction
+
+Since crossover rate didn't have an effect we decided to test the scenario when loci have a certain interaction between them.
+In real genomes mutations often have different fitness effects depending on the genetic background i.e.
+the presence of other mutations.
+Thus, linkage can be advantageous if specific combinations of mutations are better kept together because of their reinforcing effect on each other.
+In this simulation we kept the same fitness function as before but also rewarded sequences of the benefitial allele.
+For example, in the summer an individual with chromosome 010101 would have a fitness of 3 while an individual with chromosome 011000 would have a fitness of 2 + 2 (for the longest sequence in the genome) which would then outcompete the former individual eventhough the total number of 1's is less.
+
+```{r}
+setwd(here::here("results/mut_interaction"))
+values = c("c_0.5_new", "c_0.05_new", "c_0.5_num", "c_0.05_num")
+b <- do_analysis(values, "Generations per semester", "none", "b3")
+```
+
 ```{r, fig.height = 3, fig.width = 8 , fig.cap = 'A density plot of the allele frequencies at the final generation \\label{density_combined}', message = FALSE, echo = FALSE}
@@
 
-## Seasonal balance
-
-## Population size
-
 # Discussion

### 2019-12-02 writing/manuscript.Rmd
Introduction and abstract

--- 2019-12-02 writing/manuscript.Rmd
@@
 # Abstract
+Understanding the mechanisms of preserving genetic diversity is paramount to predicting the capacity of organisms to adapt to changing environmental conditions.
+In environments characterized by seasonal fluctuations, certain alleles may be beneficial under certain conditions and harmful in other environments.
+This fluctuation of additive benefits results in a strong directional selection that varies according to the season.
+@Bergland2014 experimentally observed that seasonal variation is able to preserve polymorphisms that maintain genetic diversity.
+@Wittman2017 modeled how allelic dominance changes according to the season in an organism to account for different seasonal life-history strategies.
+They present a term called “segregation lift” which describes instances of seasonal allele-fluctuations which serve to maintain genetic diversity over time.
+In this paper, we build upon the @Wittman2017 model, using the same parameters to study how genetic linkage and seasonal balance may affect segregation lift.
+The @Wittman2017 model found that in an unlinked genome the dominance parameter needed to be greater than 0.5 for segregation lift to occur.
+Our model suggests that in diploid organisms exhibiting genetic linkage, segregation lift occured when dominance=0.5, suggesting that multilocus polymorphisms are maintained if, at a certain locus, one allele over the other  is beneficial during one season.
 

### 2019-12-02 writing/manuscript.Rmd

--- 2019-12-02 writing/manuscript.Rmd
@@
 # Abstract
+Understanding the mechanisms of preserving genetic diversity is paramount to predicting the capacity of organisms to adapt to changing environmental conditions.
+In environments characterized by seasonal fluctuations, certain alleles may be beneficial under certain conditions and harmful in other environments.
+This fluctuation of additive benefits results in a strong directional selection that varies according to the season.
+@Bergland2014 experimentally observed that seasonal variation is able to preserve polymorphisms that maintain genetic diversity.
+@Wittman2017 modeled how allelic dominance changes according to the season in an organism to account for different seasonal life-history strategies.
+They present a term called “segregation lift” which describes instances of seasonal allele-fluctuations which serve to maintain genetic diversity over time.
+In this paper, we build upon the @Wittman2017 model, using the same parameters to study how genetic linkage and seasonal balance may affect segregation lift.
+The @Wittman2017 model found that in an unlinked genome the dominance parameter needed to be greater than 0.5 for segregation lift to occur.
+Our model suggests that in diploid organisms exhibiting genetic linkage, segregation lift occured when dominance=0.5, suggesting that multilocus polymorphisms are maintained if, at a certain locus, one allele over the other  is beneficial during one season.
 
 # Introduction
-Something about an orchard in Pennsylvania [@Bergland2014]. As an example of how to cite.
+
+Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2014].
+Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016].
+Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].
+Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].
+
+There has been some debate regarding whether balancing selection is capable of maintaining genetic polymorphisms in highly variable environments, and it is often thought that  this mechanism alone is not enough to maintain balanced polymorphism.
+(@Asthana2005, @Hedrick).
+However a study by @Bergland2014 observing Drosophila melanogaster in a temperate Pennsyvanian orchard revealed that strong seasonal selection can drive balancing selection favoring different life history traits over a short time span.
+These results suggest that seasonal variation contributes to the maintenance of two alleles to be present at the same loci long-term.
+If there is no fitness cost associated with polymorphic variation and there is a benefit gained through heterozygosity, then it is suggested that that balancing selection could preserve genetic variation [@Asthana2005, @Wittman2017].
+
+@Wittman2017 created a model simulating the seasonal selection observed by @Bergland2014 to clarify the role this allelic fluctuation plays in maintaining multilocus polymorphisms.
+This model introduces the term “segregation lift” which considers the importance of dominance in maintaining polymorphism across many loci in the genome and proposes that segregation lift plays an important role in preserving genetic variation.
+
+Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
+We study how rate of crossover, epistasis, allelic dominance, and seasonal balance contributes to segregation lift.
 

### 2019-12-03 writing/manuscript.Rmd
corrected references

@@
 @Bergland2014 experimentally observed that seasonal variation is able to preserve polymorphisms that maintain genetic diversity.
-@Wittman2017 modeled how allelic dominance changes according to the season in an organism to account for different seasonal life-history strategies.
+@Wittmann2017 modeled how allelic dominance changes according to the season in an organism to account for different seasonal life-history strategies.
 They present a term called “segregation lift” which describes instances of seasonal allele-fluctuations which serve to maintain genetic diversity over time.
-In this paper, we build upon the @Wittman2017 model, using the same parameters to study how genetic linkage and seasonal balance may affect segregation lift.
-The @Wittman2017 model found that in an unlinked genome the dominance parameter needed to be greater than 0.5 for segregation lift to occur.
+In this paper, we build upon the @Wittmann2017 model, using the same parameters to study how genetic linkage and seasonal balance may affect segregation lift.
+The @Wittmann2017 model found that in an unlinked genome the dominance parameter needed to be greater than 0.5 for segregation lift to occur.
 Our model suggests that in diploid organisms exhibiting genetic linkage, segregation lift occured when dominance=0.5, suggesting that multilocus polymorphisms are maintained if, at a certain locus, one allele over the other  is beneficial during one season.
@@
 
-Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2014].
+Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2010].
 Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016].
@@
 There has been some debate regarding whether balancing selection is capable of maintaining genetic polymorphisms in highly variable environments, and it is often thought that  this mechanism alone is not enough to maintain balanced polymorphism.
-(@Asthana2005, @Hedrick).
+(@Asthana2005, @PhilipW.HedrickMichaelE.Ginevan1972).
 However a study by @Bergland2014 observing Drosophila melanogaster in a temperate Pennsyvanian orchard revealed that strong seasonal selection can drive balancing selection favoring different life history traits over a short time span.
 These results suggest that seasonal variation contributes to the maintenance of two alleles to be present at the same loci long-term.
-If there is no fitness cost associated with polymorphic variation and there is a benefit gained through heterozygosity, then it is suggested that that balancing selection could preserve genetic variation [@Asthana2005, @Wittman2017].
+If there is no fitness cost associated with polymorphic variation and there is a benefit gained through heterozygosity, then it is suggested that that balancing selection could preserve genetic variation [@Asthana2005, @Wittmann2017].
 
-@Wittman2017 created a model simulating the seasonal selection observed by @Bergland2014 to clarify the role this allelic fluctuation plays in maintaining multilocus polymorphisms.
+@Wittmann2017 created a model simulating the seasonal selection observed by @Bergland2014 to clarify the role this allelic fluctuation plays in maintaining multilocus polymorphisms.
 This model introduces the term “segregation lift” which considers the importance of dominance in maintaining polymorphism across many loci in the genome and proposes that segregation lift plays an important role in preserving genetic variation.
 
-Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
+Our model recreates and builds upon the work of @Wittmann2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
 We study how rate of crossover, epistasis, allelic dominance, and seasonal balance contributes to segregation lift.

### 2019-12-03 writing/manuscript.Rmd
parameter changes in text table

--- 2019-12-02 writing/manuscript.Rmd
@@
 $$
-z = n_{homo} + d * n_{het}
+z = n_{hom} + d * n_{het}
 $$
-where $n_{homo}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci.
+where $n_{hom}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci.
 A dominance parameter of greater than one ($d > 1$) would correspond to a traditional heterozygote advantage, and therefore is not of interest in this model.
@@
 | Dominance                        | 0.5       |
-| Years                            | 100       |
+| Years                            | 300       |
 | Generations per year             | 20        |
@@
 
-```{r, fig.width = 10}
-# Small fig.width
-knitr::include_graphics("G10.png")
-knitr::include_graphics("G50.png")
-```
+# ```{r, fig.width = 10}
+# # Small fig.width
+# knitr::include_graphics("G10.png")
+# knitr::include_graphics("G50.png")
+# ```
 

### 2019-12-03 writing/manuscript.Rmd
alternative values added to table

@@
 
-| Default Parameters               |           |
-|----------------------------------|-----------|
-| Crossover probability            | 0.05      |
-| Mutation probability             | $10^{-4}$ |
-| Population size                  | 500       |
-| Number of loci                   | 100       |
-| Exponent of the fitness function | 1         |
-| Dominance                        | 0.5       |
-| Years                            | 300       |
-| Generations per year             | 20        |
-| Seasonal balance                 | 2         |
+| Parameters                       | Default   | Alternatives values      |
+|----------------------------------|-----------| -------------------------|
+| Crossover probability            | 0.05      | 0, 0.001, 0.01, 0.1, 0.5 |
+| Generations per year             | 20        | 10, 20, 50               |
+| Seasonal balance                 | 2         | 1.25, 1.5                |
+| Population size                  | 500       | 100 1000                 |
+| Exponent of the fitness function | 1         | 0.5, 2                   |
+| Dominance                        | 0.5       | 0.2, 0.8                 |
+| Mutation probability             | $10^{-4}$ |                          |
+| Number of loci                   | 100       |                          |
+| Years                            | 300       |                          |
+
+Table: Default values are a list the values that were used generally for each simulation run.
+The alternative values are values that were used to determine the affect of each variable individually.
+Some alternatives were tested in combination -- maybe explain which ones were tested in combination.
 

### 2019-12-04 writing/manuscript.Rmd
changed figure references

@@
 ```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter.
-\\label{epi_density}', message = FALSE, echo = FALSE}
+\\label{cross_density}', message = FALSE, echo = FALSE}
 setwd(here::here("results/cross_over"))
@@
 ```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year.
-\\label{gen_density}', message = FALSE, echo = FALSE}
+\\label{sb_density}', message = FALSE, echo = FALSE}
 setwd(here::here("results/seasonal_balance"))

### 2019-12-04 writing/manuscript.Rmd
epistasis function added to the methods section intro
added sentance to introducttion

@@
 Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016].
-Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].
+Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016].
 Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].
 
-There has been some debate regarding whether balancing selection is capable of maintaining genetic polymorphisms in highly variable environments, and it is often thought that  this mechanism alone is not enough to maintain balanced polymorphism.
-(@Asthana2005, @PhilipW.HedrickMichaelE.Ginevan1972).
-However a study by @Bergland2014 observing Drosophila melanogaster in a temperate Pennsyvanian orchard revealed that strong seasonal selection can drive balancing selection favoring different life history traits over a short time span.
+There has been some debate regarding whether balancing selection is capable of maintaining genetic polymorphisms in highly variable environments, and it is often thought that  this mechanism alone is not enough to maintain balanced polymorphism (@Asthana2005, @PhilipW.HedrickMichaelE.Ginevan1972).
+A study by @Bergland2014 observing _Drosophila _melanogaster_ in a temperate Pennsyvanian orchard revealed that strong seasonal selection can drive balancing selection favoring different life history traits over a short time span.
 These results suggest that seasonal variation contributes to the maintenance of two alleles to be present at the same loci long-term.
@@
 A dominance parameter of greater than one ($d > 1$) would correspond to a traditional heterozygote advantage, and therefore is not of interest in this model.
+
+The fitness is calculated according to the equation: 
+$$
+w(z) = (1+z)^y
+$$
+where $w(z)$ is the fitness of a particular z score.
+The exponent here is introduced to allow for non-linear interaction between genotype and fitness, an interaction that approximates the affect of epistasis.
 

### 2019-12-04 writing/manuscript.Rmd
tiny edits
Cleaned up results.

@@
 author: \emph{Thomas O'Leary, Csenge Petak, Alison Hall}
+date: "`r format(Sys.time(), '%d %B %Y')`"
 output: 
@@
 
-Our model recreates and builds upon the work of @Wittmann2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
-We study how rate of crossover, epistasis, allelic dominance, and seasonal balance contributes to segregation lift.
+Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
+We study how rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contributes to segregation lift.
+Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
 
@@
 
+## Interaction between loci: an alternative scenario
+
+We decided to test the scenario when loci have a certain interaction between them.
+In real genomes mutations often have different fitness effects depending on the genetic background i.e.
+the presence of other mutations.
+Thus, linkage can be advantageous if specific combinations of mutations are better kept together because of their reinforcing effect on each other.
+In this simulation we kept the same fitness function as before but also rewarded sequences of repeated values of the benefitial allele.
+For example, in the summer an individual with chromosome 01010101 would have a fitness of 4 for the number of 1's + 1 for the longest sequence of 1's, while an individual with chromosome 01110000 would have a fitness of 3 + 3 which would then outcompete the former individual eventhough the total number of 1's is less.
+
 # Results
+
+We compared the effect of different variables by looking at the allele frequencies at the last generation of the simulation and calculated the standard deviation (the higher this value the less balancing polymorphism was present in the population) and proportion of fixed loci.
+Since we had 5 repetitions for each parameter value we used an Analysis of Variance (ANOVA) to look for significant differences.
 
@@
 cross-over happens at every loci) both the proportion of fixed loci (p = 2.52e-07) and standard deviation of loci frequencies (p = 4.63e-07) are lower when dominance is 0.8 compared to when dominance is 0.5.
+See Figures \ref{dom_0.05_1} and \ref{dom_0.05_2}.
 
-```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter.
-\\label{cross_density}', message = FALSE, echo = FALSE}
+```{r, fig.height = 10, fig.width = 8, fig.cap = 'Summer allele frequency at each loci over time.
+(A) When d = 0.8 fixation of a few alleles start only after about 700 generations and most alleles finish with frequencies closer to 0.5.
+(B) On the other hand, when d = 0.5 fixation starts as soon as 200 generations and most alleles fixate or get very close to fixation by the end of the simulation.
+\\label{dom_0.05_1}', message = FALSE, echo = FALSE}
+setwd(here::here("results/cross_over"))
+
+# get a list of the files that match the variable value of interest
+value <- "d_0.8_y_1_c_0.5"
+
+# which rep do you want to look at? 
+rep <- 4
+
+# find files that match and create figure captions with parameter details
+files <- list.files()[grep(value, list.files())]
+names <- str_remove(files, ".csv")
+param <- str_split(names, "_", simplify = TRUE)[,c(3,5,7,9,11,13,15,18)]
+caption <- paste(paste("Generations per year", param[rep, 1]),
+                paste("Pop size", param[rep, 2]),
+                paste("Seasonal Balance", param[rep, 3]),
+                paste("Number of Loci", param[rep, 4]),
+                paste("\nDominance", param[rep, 5]),
+                paste("Epistasis", param[rep, 6]),
+                paste("Crossover probability", param[rep, 7]),
+                paste("Replicate number", param[rep, 8]), sep = "; ")
+
+# read in file and plot results
+sim_results <- read.csv(files[rep])
+
+# plot results less than generation 2000 and divisible by 10 to get only the 
+# freq at the seasonal turns for gen/year = 20
+p1 <- sim_results %>%
+  filter(genz < 2000 & genz %% 10 == 0) %>%
+  plot_freq(figure_caption = caption, fig_title = "Dominance = 0.8, no linkage" )
+
+setwd(here::here("results/cross_over"))
+
+# get a list of the files that match the variable value of interest
+value <- "d_0.5_y_1_c_0.5"
+
+# which rep do you want to look at? 
+rep <- 3
+
+# find files that match and create figure captions with parameter details
+files <- list.files()[grep(value, list.files())]
+names <- str_remove(files, ".csv")
+param <- str_split(names, "_", simplify = TRUE)[,c(3,5,7,9,11,13,15,18)]
+caption <- paste(paste("Generations per year", param[rep, 1]),
+                paste("Pop size", param[rep, 2]),
+                paste("Seasonal Balance", param[rep, 3]),
+                paste("Number of Loci", param[rep, 4]),
+                paste("\nDominance", param[rep, 5]),
+                paste("Epistasis", param[rep, 6]),
+                paste("Crossover probability", param[rep, 7]),
+                paste("Replicate number", param[rep, 8]), sep = "; ")
+
+# read in file and plot results
+sim_results <- read.csv(files[rep])
+
+# plot results less than generation 2000 and divisible by 10 to get only the 
+# freq at the seasonal turns for gen/year = 20
+p2 <- sim_results %>%
+  filter(genz < 2000 & genz %% 10 == 0) %>%
+  plot_freq(figure_caption = caption, fig_title = "Dominance = 0.5, no linkage" )
+
+plot_grid(p1, p2, nrow = 2, ncol = 1, labels = "AUTO")
+```
+
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the dominance parameter.
+\\label{dom_0.05_2}', message = FALSE, echo = FALSE}
 setwd(here::here("results/cross_over"))
@@
 
-```{r, fig.width = 10}
-# Small fig.width
-knitr::include_graphics("D05C05.png")
-knitr::include_graphics("D08C05.png")
-```
+Then, we started playing with different parameters.
 
-Then, we started playing with different parameters.
 ## Crossover rate
@@
 Crossover rate didn't seem to have an effect at all in terms of standard deviation (p = 0.123) and proportion of fixed loci (p = 0.462).
-Our hypothesis is that crossover didn't have an effect because two opposing forces created by it canceled out.
-First of all, higher crossover rates creates more genetic variation in the population "helping" selection but on the other hand it also creates stochasticity since a selected high fitness individual can pass on an unfit chromosome after crossover by chance.
-
-When there was no crossover and so linkage was maximized there was a much bigger variation in the proportion of fixed loci in the last generation.
-This could be because since in this case the only way for an individual to change was through mutations, which is pretty infrequent, if the starting population contained a lot of individuals with more of one allele than the other many loci went to fixation while in a starting population with individuals whose genomes contained 50%-50% of the two alleles balancing polymorphism could be maintained more successfully.
+The greates variation in both measures was when there was no crossover introduced at all and changes in the chromosomes were only due to mutations.
+See Figure \ref{crossover_box}.
 
@@
 values = c("c_0_", "c_0.001", "c_0.01_", "c_0.05","c_0.1", "d_0.5_y_1_c_0.5_")
-b <- do_analysis(values, "Dominance", "c_", "b3")
+b <- do_analysis(values, "Crossover rates", "c_", "b3")
 ```
-```{r, echo = FALSE}
+```{r, fig.height = 5, fig.width = 8, fig.cap = 'Different crossover rates did not effect the allele frequency distribution at the end of the simulations.
+\\label{crossover_box}', message = FALSE, echo = FALSE}
 b
@@
 Since the crossover rate didn't have an effect on whether or not balanced polymorphism is achieved, our tests with different dominance values resulted in the same dynamics as when we tested with crossover rate 0.5.
+See Figure \ref{dom_density}.
 
-This is how you reference Figure \ref{dom_density} in the text.
-
-```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of dominance.
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of dominance with a crossover rate of 0.05.
 \\label{dom_density}', message = FALSE, echo = FALSE}
@@
 
-Under default crossover rate (0.05) epistasis didn't have an effect (standard deviation p = 0.986, proportion of fixed alleles p = 0.613).
-
-This is how you reference Figure \ref{epi_density} in the text.
+Under default crossover rate (0.05) epistasis didn't have an effect (standard deviation p = 0.986, proportion of fixed alleles p = 0.613). See Figure \ref{epi_density}.
 
@@
 
-When the generations per season was 10, the standard deviation was significantly lower than for longer generation times per season (p = 0.00161).
-We hypothise that with more generations per season loci were under selection for a longer period of time and thus were more likely to go to fixation at one point.
+When the generations per season was 10, the standard deviation was significantly lower than for longer generation times per season (p = 0.00161). See Figure \ref{gens}.
 
-This is how you reference Figure \ref{gen_density} in the text.
-
-```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year.
-\\label{gen_density}', message = FALSE, echo = FALSE}
+```{r, fig.height = 10, fig.width = 8, fig.cap = 'Summer allele frequency at each loci over time.
+When the generation time is shorter the allele frequencies oscilate less over time as they experience selection for a shorter period of time.
+Thus, alleles are less likely to go to fixation.\\label{gens}', message = FALSE, echo = FALSE}
 setwd(here::here("results/generations"))
 
-# load all files and filter only the final generation
-all_tbl <- list.files() %>% 
-  map_df(~read_plus(.))
+# get a list of the files that match the variable value of interest
+value <- "G_10"
 
-tbl_max_gen <- all_tbl %>%
-  split(.$filename) %>%
-  map(function(.data){filter(.data, genz == max(genz))}) %>%
-  do.call("rbind", .)
+# which rep do you want to look at? 
+rep <- 2
 
-# plot the density distribution
-p3 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
-        geom_density(alpha = 0.2) + 
-        scale_fill_manual(values = c(rep("#e25dbb", 5), 
-                                     rep("#6cdf4c", 5),
-                                     rep("#258bd2", 5)),
-                          breaks = unique(all_tbl$filename)[c(1,6,11)],
-                          # legend name
-                          name = "Generations\nper year",
-                          # values tested
-                          labels = c("10", "20", "50")) +
-        ylab("Density") + 
-        xlab("Allele Frequency") +
-        theme_classic()
+# find files that match and create figure captions with parameter details
+files <- list.files()[grep(value, list.files())]
+names <- str_remove(files, ".csv")
+param <- str_split(names, "_", simplify = TRUE)[,c(3,5,7,9,11,13,15,18)]
+caption <- paste(paste("Generations per year", param[rep, 1]),
+                paste("Pop size", param[rep, 2]),
+                paste("Seasonal Balance", param[rep, 3]),
+                paste("Number of Loci", param[rep, 4]),
+                paste("\nDominance", param[rep, 5]),
+                paste("Epistasis", param[rep, 6]),
+                paste("Crossover probability", param[rep, 7]),
+                paste("Replicate number", param[rep, 8]), sep = "; ")
 
-print(p3)
+# read in file and plot results
+sim_results <- read.csv(files[rep])
+
+# plot results less than generation 2000 and divisible by 10 to get only the 
+# freq at the seasonal turns for gen/year = 20
+p1 <- sim_results %>%
+  filter(genz < 2000 & genz %% 10 == 0) %>%
+  plot_freq(figure_caption = caption, fig_title = "Generations per year = 10" )
+
+setwd(here::here("results/generations"))
+
+# get a list of the files that match the variable value of interest
+value <- "G_50"
+
+# which rep do you want to look at? 
+rep <- 1
+
+# find files that match and create figure captions with parameter details
+files <- list.files()[grep(value, list.files())]
+names <- str_remove(files, ".csv")
+param <- str_split(names, "_", simplify = TRUE)[,c(3,5,7,9,11,13,15,18)]
+caption <- paste(paste("Generations per year", param[rep, 1]),
+                paste("Pop size", param[rep, 2]),
+                paste("Seasonal Balance", param[rep, 3]),
+                paste("Number of Loci", param[rep, 4]),
+                paste("\nDominance", param[rep, 5]),
+                paste("Epistasis", param[rep, 6]),
+                paste("Crossover probability", param[rep, 7]),
+                paste("Replicate number", param[rep, 8]), sep = "; ")
+
+# read in file and plot results
+sim_results <- read.csv(files[rep])
+
+# plot results less than generation 2000 and divisible by 10 to get only the 
+# freq at the seasonal turns for gen/year = 20
+p2 <- sim_results %>%
+  filter(genz < 2000 & genz %% 10 == 0) %>%
+  plot_freq(figure_caption = caption, fig_title = "Generations per year = 50" )
+
+plot_grid(p1, p2, nrow = 2, ncol = 1, labels = "AUTO")
 ```
-
-# ```{r, fig.width = 10}
-# # Small fig.width
-# knitr::include_graphics("G10.png")
-# knitr::include_graphics("G50.png")
-# ```
 
@@
 Purely by changing population size from 100 to 1000 average proportion of fixed loci decreased from 0.9 to 0.3.
-This is probably due to the effect of random genetic drift; when the population is small alleles go to fixation due to the large effect of drift.
+See Figure \ref{pop}.
 
-```{r}
+```{r, message = FALSE, include=FALSE}
 setwd(here::here("results/pop_size"))
 values = c("Ps_100_", "Ps_500", "Ps_1000")
-b <- do_analysis(values, "Generations per semester", "Ps_", "b3")
+b <- do_analysis(values, "Population size", "Ps_", "b3")
 ```
-```{r, echo = FALSE}
+```{r, fig.height = 5, fig.width = 6, fig.cap = 'Population size had a dramatic effect on both standard deviation and proportion of fixed loci.  \\label{pop}', message = FALSE, echo = FALSE}
 b
@@
 
-Interestingly, having a season that has more generations than in the other didn't result in a higher proportion of fixed alleles as one whould have expected (p = 0.289).
-Rather, while alleles fixed by reaching frequencies of 0 or 1 in the case where both seasons had equal number of generations (seasonal balance = 2) when there were more generations in one more alleles had frequencies of 1 than 0 but the overall proportion stayed the same.
+Having a season that has more generations than the other didn't result in a higher proportion of fixed alleles (p = 0.289).
+Rather, while when both seasons had equal number of generations (seasonal balance = 2) alleles fixed by reaching frequencies of either 0 or 1, when summer had more generations more alleles had frequencies of 1 than 0, but the overall proportion stayed the same.
+See Figure \ref{sb_density}.
 
-```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year.
+```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the seasonal balance parameter.
 \\label{sb_density}', message = FALSE, echo = FALSE}
@@
                           # legend name
-                          name = "Generations\nper year",
+                          name = "Seasonal balance",
                           # values tested
@@
 
-Since crossover rate didn't have an effect we decided to test the scenario when loci have a certain interaction between them.
-In real genomes mutations often have different fitness effects depending on the genetic background i.e.
-the presence of other mutations.
-Thus, linkage can be advantageous if specific combinations of mutations are better kept together because of their reinforcing effect on each other.
-In this simulation we kept the same fitness function as before but also rewarded sequences of the benefitial allele.
-For example, in the summer an individual with chromosome 010101 would have a fitness of 3 while an individual with chromosome 011000 would have a fitness of 2 + 2 (for the longest sequence in the genome) which would then outcompete the former individual eventhough the total number of 1's is less.
+Introducing interaction between loci made seasonal balance to be reached more difficult.
+Every variable kept the same the new simulation produced a higher average standard deviation of allele frequencies (p = 3.58e-05) and proportion of fixed loci (p = 7.76e-06) regardless of crossover rate.
+See Figure \ref{int}.
 
-```{r}
+```{r, message = FALSE, include=FALSE}
 setwd(here::here("results/mut_interaction"))
 values = c("c_0.5_new", "c_0.05_new", "c_0.5_num", "c_0.05_num")
-b <- do_analysis(values, "Generations per semester", "none", "b3")
+b <- do_analysis(values, "Crossover rate and type of simulation", "none", "b3")
 ```
-
-```{r, fig.height = 3, fig.width = 8 , fig.cap = 'A density plot of the allele frequencies at the final generation \\label{density_combined}', message = FALSE, echo = FALSE}
-
-# this is how you could potentially mash a few figures together in the same plot
-plot_grid(p1, p2, labels = "AUTO")
+```{r, fig.height = 5, fig.width = 6, fig.cap = 'Interaction between loci increased proportion of fixed loci regardless of crossover rate.  \\label{int}', message = FALSE, echo = FALSE}
+b
 ```
@@
 
+## Crossover rate
+
+Crossover rate didn't have an effect on seasonal balance.
+Our hypothesis is that two opposing forces created by it canceled out.
+First of all, higher crossover rates create more genetic variation in the population "helping" selection but on the other hand it also creates stochasticity since a selected high fitness individual can pass on an unfit chromosome after crossover by chance.
+
+When there was no crossover and so linkage was maximized there was a much bigger variation in the proportion of fixed loci in the last generation.
+This could be because since in this case the only way for an individual to change was through mutations, which is pretty infrequent, and if the starting population contained a lot of individuals with more of one allele than the other many loci went to fixation while in a starting population with individuals whose genomes contained 50%-50% of the two alleles balancing polymorphism could be maintained more successfully.
+
+## Epistasis
+
+We’ll think more about an explanation on why epistasis didn’t have an effect.
+
+## Generation
+
+We hypothesize that when the generation time is shorter the allele frequencies oscillate less over time as they experience selection for a shorter period of time.
+Thus, alleles are less likely to go to fixation.
+
+## Population size
+
+Population size had the greatest effect of all the variables we tested.
+This is probably due to the effect of random genetic drift; when the population is small alleles go to fixation due to the large effect of drift.
+
+## Mutational interaction
+
+We’ll think more about an explanation on why even here crossover didn’t seem to have an effect.
+
 # References

### 2019-12-04 writing/manuscript.Rmd
greatest version

@@
 Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016].
-Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016].
+Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].
+Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016].
 Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].
@@
 Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population.
-We study how rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contributes to segregation lift.
+We study how the rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contribute to segregation lift.
 Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.

### 2019-12-05 writing/manuscript.Rmd
added a few comments

@@
 
+# Easton comments
+
+- I was surprised that you opened the introduction with text on phenotypic plasticity. Your work really gets at genetic change from season to season, as opposed to only phenotypic changes. 
+- Good second introduction paragraph to explain the two most important papers that motivate your work
+- In your introduction, you need an additional paragraph explaining what gaps remain after the two papers you describe. This then sets up the reasons for why your study will be important 
+- Good job describing the model
+- Eventually section 3.2 could be made into a nice conceptual figure
+- Overall, your figures came out very nice. They are simple and aesthetically appealing. In the real manuscript, you won't want the figure interpretations within each caption
+- As I mentioned in class, I think there are some interesting parts of your analyses in the context of climate change predictions.
+With climate change, we expect many places to experience longer (and earlier) summers.
+In addition, generation times for some species are expected to shorten with warmer temperatures.
+To me, your results would then say that with climate change, more loci are expected to become fixed because of summer changes, but that shorter generations might present an opposing force.
+- I think your work is certainly possible.
+I am not an expert on this literature, but it does seem that you address several interesting points by focusing on epistatis, seasonal balance, and generation length.
+
+Here is what I need from you for the final project:
+
+Nothing. Your first draft is good enough. If you make edits and changes, I am happy to read additional drafts, this semester or next. Otherwise, you are done for the semester! Great work!
+
 # References

### 2019-12-12 writing/manuscript.Rmd
Small edit to begining of intro

@@
 
-Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2010].
-Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016].
+Genetic polymorphisms can provide a cache of diversity that contributes to adaptation in highly variable ecosystems [Gulisija2016].
 Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].
@@
 We study how the rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contribute to segregation lift.
-Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
+By including the metrics Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
 

### 2019-12-13 writing/manuscript.Rmd
Small changes to the introduction

@@
 Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016].
-Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].
+Understanding the role of seasonality plays in maintaining genetic polymorphisms can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].
 
@@
 We study how the rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contribute to segregation lift.
-By including the metrics Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
+Climate change models predict a change in seasonal timing, with a lengthened and earlier summer and a milder shorter winter @[Bradshaw2006].
+The seasonal balance metric allows our model to include effects of changing length of seasons to understand how a longer summer may influence segregation lift.
+Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
 
